---
title: "tj-data-prep"
author: "Francisca Castro"
date: "2022-11-22"
output: html_document
---

# Packages Installation

```{r message=FALSE, warning=FALSE}
pacman::p_load(readxl, tidyverse, dplyr, readr, BBmisc, xlsx, haven,
               formattable, writexl, countrycode, panelView, countrycode, magrittr)
```

# Data preparation

## Afrobarometer

Extract variables of interest and form a new dataframe

### Wave 1

```{r}
afrobarometer_w1 <- read_sav("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/afro-barometer/AFB_Merged_R1.sav")

afrobarometer_w1$country <- as.numeric(afrobarometer_w1$country)
afrobarometer_w1 %<>%
  mutate(country = recode(country,
                          "1" = "Botswana",
                          "2" = "Ghana",
                          "3" = "Lesotho",
                          "4" = "Malawi",
                          "5" = "Mali",
                          "6" = "Namibia",
                          "7" = "Nigeria",
                          "8" = "South Africa",
                          "9" = "Tanzania",
                          "10" = "Uganda",
                          "11" = "Zambia",
                          "12" = "Zimbabwe"))
table(afrobarometer_w1$country)

afrobarometer_w1$year <- 0
afrobarometer_w1$year[afrobarometer_w1$country == "Botswana"] <- "1999"
afrobarometer_w1$year[afrobarometer_w1$country == "Ghana"] <- "1999"
afrobarometer_w1$year[afrobarometer_w1$country == "Lesotho"] <- "2000"
afrobarometer_w1$year[afrobarometer_w1$country == "Malawi"] <- "1999"
afrobarometer_w1$year[afrobarometer_w1$country == "Mali"] <- "2001"
afrobarometer_w1$year[afrobarometer_w1$country == "Namibia"] <- "1999"
afrobarometer_w1$year[afrobarometer_w1$country == "Nigeria"] <- "1999"
afrobarometer_w1$year[afrobarometer_w1$country == "South Africa"] <- "2000"
afrobarometer_w1$year[afrobarometer_w1$country == "Tanzania"] <- "2001"
afrobarometer_w1$year[afrobarometer_w1$country ==  "Uganda"] <- "2000"
afrobarometer_w1$year[afrobarometer_w1$country ==  "Zambia"] <- "1999"
afrobarometer_w1$year[afrobarometer_w1$country ==  "Zimbabwe"] <- "1999"

afrobarometer_w1$survey <- 'afrobarometer_w1'

afrobarometer_w1 %<>%
  mutate(fight_corr = case_when(pfpcr1 == 4 ~ 1,
                                pfpcr1 == 3 ~ 2,
                                pfpcr1 == 2 ~ 3,
                                pfpcr1 == 1 ~ 4),
         corr_leaders = case_when(pfpcr3 == 4 ~ 1,
                                  pfpcr3 == 3 ~ 2,
                                  pfpcr3 == 2 ~ 3,
                                  pfpcr3 == 1 ~ 4)) %>%
  purrr::modify_at(c("fight_corr", "corr_leaders"), factor) %>%
  select(country, year, fight_corr, corr_leaders, survey) 
```

### Wave 2

```{r}
afrobarometer_w2 <- read_sav("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/afro-barometer/AFB_Merged_R2.sav")

afrobarometer_w2$year <- format(as.Date(afrobarometer_w2$dateintr, format="%Y-%m-%d"),"%Y")
class(afrobarometer_w2$year)
afrobarometer_w2$year <- as.numeric(afrobarometer_w2$year)

afrobarometer_w2$survey <- 'afrobarometer_w2'

afrobarometer_w2$country <- as.numeric(afrobarometer_w2$country)
afrobarometer_w2 %<>%
  mutate(country = recode(country,
                          "1" = "Botswana",
                          "2" = "Ghana",
                          "3" = "Lesotho",
                          "4" = "Malawi",
                          "5" = "Mali",
                          "6" = "Namibia",
                          "7" = "Nigeria",
                          "8" = "South Africa",
                          "9" = "Tanzania",
                          "10" = "Uganda",
                          "11" = "Zambia",
                          "12" = "Zimbabwe",
                          "13" = "Cape Verde",
                          "14" = "Kenya",
                          "15" = "Mozambique",
                          "16" = "Senegal"))
table(afrobarometer_w2$country)

afrobarometer_w2$year[afrobarometer_w2$country ==  "Senegal"] <- "2002"

afrobarometer_w2 %<>%
  mutate(corr_pres = case_when(q51a == 0 ~ 1, #none
                               q51a == 1 ~ 2,
                               q51a == 2 ~ 3,
                               q51a == 3 ~ 4), #all of them
         corr_gov = case_when(q51c == 0 ~ 1, #none
                              q51c == 1 ~ 2,
                              q51c == 2 ~ 3,
                              q51c == 3 ~ 4), #all of them
         corr_jud = case_when(q51f == 0 ~ 1, #none
                              q51f == 1 ~ 2,
                              q51f == 2 ~ 3,
                              q51f == 3 ~ 4), #all of them
         fight_corr = case_when(q45j == 1 ~ 1, #1 very badly
                                q45j == 2 ~ 2,
                                q45j == 3 ~ 3,
                                q45j == 4 ~ 4), #4 very well
         corr_leaders = case_when(q51b == 0 ~ 1, #none of them
                                  q51b == 1 ~ 2,
                                  q51b == 2 ~ 3,
                                  q51b == 3 ~ 4)) %>% # all of them
  purrr::modify_at(c('corr_pres', 'corr_gov', 'corr_jud', "fight_corr", 
                     "corr_leaders"), factor) %>%
  select(country, year, corr_pres, corr_gov, corr_jud, fight_corr, corr_leaders, survey) 

```

### Wave 3

```{r}
afrobarometer_w3 <- read_sav("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/afro-barometer/AFB_Merged_R3.sav")

afrobarometer_w3$year <- format(as.Date(afrobarometer_w3$dateintr, format="%Y-%m-%d"),"%Y")
table(afrobarometer_w3$year)
table(afrobarometer_w3$year, afrobarometer_w3$country)

afrobarometer_w3$survey <- 'afrobarometer_w3'

afrobarometer_w3$country <- as.numeric(afrobarometer_w3$country)

afrobarometer_w3 %<>%
  mutate(country = recode(country,
                          "1" = "Benin",
                          "2" = "Botswana",
                          "3" = "Cape Verde",
                          "4" = "Ghana",
                          "5" = "Kenya",
                          "6" = "Lesotho",
                          "7" = "Madagascar",
                          "8" = "Malawi",
                          "9" = "Mali",
                          "10" = "Mozambique",
                          "11" = "Namibia",
                          "12" = "Nigeria",
                          "13" = "Senegal",
                          "14" = "South Africa",
                          "15" = "Tanzania",
                          "16" = "Uganda",
                          "17" = "Zambia",
                          "18" = "Zimbabwe"))

afrobarometer_w3 %<>%
  mutate(corr_pres = case_when(q56a == 0 ~ 1, #none
                               q56a == 1 ~ 2,
                               q56a == 2 ~ 3,
                               q56a == 3 ~ 4), #all of them
         corr_gov = case_when(q56d == 0 ~ 1, #none
                              q56d == 1 ~ 2,
                              q56d == 2 ~ 3,
                              q56d == 3 ~ 4), #all of them
         corr_jud = case_when(q56h == 0 ~ 1, #none
                              q56h == 1 ~ 2,
                              q56h == 2 ~ 3,
                              q56h == 3 ~ 4), #all of them
         fight_corr = case_when(q65j == 1 ~ 1, #1 very badly
                                q65j == 2 ~ 2,
                                q65j == 3 ~ 3,
                                q65j == 4 ~ 4), #4 very well
         corr_leaders = case_when(q56b == 0 ~ 1, #none of them
                                  q56b == 1 ~ 2,
                                  q56b == 2 ~ 3,
                                  q56b == 3 ~ 4)) %>% # all of them
  purrr::modify_at(c('corr_pres', 'corr_gov', 'corr_jud', "fight_corr", 
                     "corr_leaders"), factor) %>%
  select(country, year, corr_pres, corr_gov, corr_jud, fight_corr, corr_leaders, survey) 

```

### Wave 4

```{r}
afrobarometer_w4 <- read_sav("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/afro-barometer/AFB_Merged_R4.sav")

afrobarometer_w4$year <- format(as.Date(afrobarometer_w4$DATEINTR, format="%Y-%m-%d"),"%Y")
table(afrobarometer_w4$year)

afrobarometer_w4$survey <- 'afrobarometer_w4'

afrobarometer_w4$country <- as.numeric(afrobarometer_w4$COUNTRY)

afrobarometer_w4 %<>%
  mutate(country = recode(country,
                          "1" = "Benin",
                          "2" = "Botswana",
                          "3" = "Burkina Faso",
                          "4" = "Cape Verde",
                          "5" = "Ghana",
                          "6" = "Kenya",
                          "7" = "Lesotho",
                          "8" = "Liberia",
                          "9" = "Madagascar",
                          "10" = "Malawi",
                          "11" = "Mali",
                          "12" = "Mozambique",
                          "13" = "Namibia",
                          "14" = "Nigeria",
                          "15" = "Senegal",
                          "16" = "South Africa",
                          "17" = "Tanzania",
                          "18" = "Uganda",
                          "19" = "Zambia",
                          "20" = "Zimbabwe"))

afrobarometer_w4 %<>%
  mutate(corr_pres = case_when(Q50A == 0 ~ 1, #none
                               Q50A == 1 ~ 2,
                               Q50A == 2 ~ 3,
                               Q50A == 3 ~ 4), #all of them
         corr_gov = case_when(Q50D == 0 ~ 1, #none
                              Q50D == 1 ~ 2,
                              Q50D == 2 ~ 3,
                              Q50D == 3 ~ 4), #all of them
         corr_jud = case_when(Q50G == 0 ~ 1, #none
                              Q50G == 1 ~ 2,
                              Q50G == 2 ~ 3,
                              Q50G == 3 ~ 4), #all of them
         fight_corr = case_when(Q57K == 1 ~ 1, #1 very badly
                                Q57K == 2 ~ 2,
                                Q57K == 3 ~ 3,
                                Q57K == 4 ~ 4), #4 very well
         corr_leaders = case_when(Q50B == 0 ~ 1, #none of them
                                  Q50B == 1 ~ 2,
                                  Q50B == 2 ~ 3,
                                  Q50B == 3 ~ 4)) %>% # all of them
  purrr::modify_at(c('corr_pres', 'corr_gov', 'corr_jud', "fight_corr", 
                     "corr_leaders"), factor) %>%
  select(country, year, corr_pres, corr_gov, corr_jud, fight_corr, corr_leaders, survey) 
```

### Wave 5

```{r}
afrobarometer_w5 <- read_sav("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/afro-barometer/AFB_Merged_R5.sav")

afrobarometer_w5$year <- format(as.Date(afrobarometer_w5$DATEINTR, format="%Y-%m-%d"),"%Y")
table(afrobarometer_w5$year)

afrobarometer_w5$survey <- 'afrobarometer_w5'

afrobarometer_w5$country <- as.numeric(afrobarometer_w5$COUNTRY)

afrobarometer_w5 %<>%
  mutate(country = recode(country,
                          "1" = "Algeria",
                          "2" = "Benin",
                          "3" = "Botswana",
                          "4" = "Burkina Faso",
                          "5" = "Burundi",
                          "6" = "Cameroon",
                          "7" = "Cape Verde",
                          "8" = "Cote d’Ivoire",
                          "9" = "Egypt",
                          "10" = "Eswatini",
                          "11" = "Ghana",
                          "12" = "Guinea",
                          "13" = "Kenya",
                          "14" = "Lesotho",
                          "15" = "Liberia",
                          "16" = "Madagascar",
                          "17" = "Malawi",
                          "18" = "Mali",
                          "19" = "Mauritius",
                          "20" = "Morocco",
                          "21" = "Mozambique",
                          "22" = "Namibia",
                          "23" = "Niger",
                          "24" = "Nigeria",
                          "25" = "Senegal",
                          "26" = "Sierra Leone",
                          "27" = "South Africa",
                          "28" = "Sudan",
                          "29" = "Swaziland",
                          "30" = "Tanzania",
                          "31" = "Togo",
                          "32" = "Tunisia",
                          "33" = "Uganda",
                          "34" = "Zambia",
                          "35" = "Zimbabwe"))

afrobarometer_w5 %<>%
  mutate(corr_pres = case_when(Q60A == 0 ~ 1, #none
                               Q60A == 1 ~ 2,
                               Q60A == 2 ~ 3,
                               Q60A == 3 ~ 4), #all of them
         corr_gov = case_when(Q60C == 0 ~ 1, #none
                              Q60C == 1 ~ 2,
                              Q60C == 2 ~ 3,
                              Q60C == 3 ~ 4), #all of them
         fight_corr = case_when(Q65K == 1 ~ 1, #1 very badly
                                Q65K == 2 ~ 2,
                                Q65K == 3 ~ 3,
                                Q65K == 4 ~ 4), #4 very well
         corr_leaders = case_when(Q60B == 0 ~ 1, #none of them
                                  Q60B == 1 ~ 2,
                                  Q60B == 2 ~ 3,
                                  Q60B == 3 ~ 4)) %>% # all of them
  purrr::modify_at(c('corr_pres', 'corr_gov', "fight_corr", 
                     "corr_leaders"), factor) %>%
  select(country, year, corr_pres, corr_gov, fight_corr, corr_leaders, survey) 
```

### Wave 6

```{r}
afrobarometer_w6 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/afro-barometer/AFB_Merged_R6.dta")

afrobarometer_w6$year <- format(as.Date(afrobarometer_w6$DATEINTR, format="%Y-%m-%d"),"%Y")

afrobarometer_w6$survey <- 'afrobarometer_w6'

afrobarometer_w6$country <- as.numeric(afrobarometer_w6$COUNTRY)

afrobarometer_w6 %<>%
  mutate(country = recode(country,
                          "1" = "Algeria",
                          "2" = "Benin",
                          "3" = "Botswana",
                          "4" = "Burkina Faso",
                          "5" = "Burundi",
                          "6" = "Cameroon",
                          "7" = "Cape Verde",
                          "8" = "Cote d’Ivoire",
                          "9" = "Egypt",
                          "10" = "Gabon",
                          "11" = "Ghana",
                          "12" = "Guinea",
                          "13" = "Kenya",
                          "14" = "Lesotho",
                          "15" = "Liberia",
                          "16" = "Madagascar",
                          "17" = "Malawi",
                          "18" = "Mali",
                          "19" = "Mauritius",
                          "20" = "Morocco",
                          "21" = "Mozambique",
                          "22" = "Namibia",
                          "23" = "Niger",
                          "24" = "Nigeria",
                          "25" = "Sao Tomé and Príncipe",
                          "26" = "Senegal",
                          "27" = "Sierra Leone",
                          "28" = "South Africa",
                          "29" = "Sudan",
                          "30" = "Swaziland",
                          "31" = "Tanzania",
                          "32" = "Togo",
                          "33" = "Tunisia",
                          "34" = "Uganda",
                          "35" = "Zambia",
                          "36" = "Zimbabwe"))

afrobarometer_w6 %<>%
  mutate(corr_pres = case_when(Q53A == 0 ~ 1, #none
                               Q53A == 1 ~ 2,
                               Q53A == 2 ~ 3,
                               Q53A == 3 ~ 4), #all of them
         corr_gov = case_when(Q53C == 0 ~ 1, #none
                              Q53C == 1 ~ 2,
                              Q53C == 2 ~ 3,
                              Q53C == 3 ~ 4), #all of them
         corr_jud = case_when(Q53G == 0 ~ 1, #none
                              Q53G == 1 ~ 2,
                              Q53G == 2 ~ 3,
                              Q53G == 3 ~ 4), #all of them
         fight_corr = case_when(Q66K == 1 ~ 1, #1 very badly
                                Q66K == 2 ~ 2,
                                Q66K == 3 ~ 3,
                                Q66K == 4 ~ 4), #4 very well
         corr_leaders = case_when(Q53B == 0 ~ 1, #none of them
                                  Q53B == 1 ~ 2,
                                  Q53B == 2 ~ 3,
                                  Q53B == 3 ~ 4)) %>% # all of them
  purrr::modify_at(c('corr_pres', 'corr_gov', 'corr_jud', "fight_corr", 
                     "corr_leaders"), factor) %>%
  select(country, year, corr_pres, corr_gov, corr_jud, fight_corr, corr_leaders, survey) 
```

### Wave 7

```{r}
afrobarometer_w7 <- read_sav("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/afro-barometer/AFB_Merged_R7.sav")

afrobarometer_w7$year <- format(as.Date(afrobarometer_w7$DATEINTR, format="%Y-%m-%d"),"%Y")

afrobarometer_w7$survey <- 'afrobarometer_w7'

afrobarometer_w7$country <- as.numeric(afrobarometer_w7$COUNTRY)

afrobarometer_w7 %<>%
  mutate(country = recode(country,
                          "1" = "Benin",
                          "2" = "Botswana",
                          "3" = "Burkina Faso",
                          "4" = "Cape Verde",
                          "5" = "Cameroon",
                          "6" = "Cote d’Ivoire",
                          "7" = "Swaziland",
                          "8" = "Gabon",
                          "9" = "Gambia",
                          "10" = "Ghana",
                          "11" = "Guinea",
                          "12" = "Kenya",
                          "13" = "Lesotho",
                          "14" = "Liberia",
                          "15" = "Madagascar",
                          "16" = "Malawi",
                          "17" = "Mali",
                          "18" = "Mauritius",
                          "19" = "Morocco",
                          "20" = "Mozambique",
                          "21" = "Namibia",
                          "22" = "Niger",
                          "23" = "Nigeria",
                          "24" = "Sao Tomé and Príncipe",
                          "25" = "Senegal",
                          "26" = "Sierra Leone",
                          "27" = "South Africa",
                          "28" = "Sudan",
                          "29" = "Tanzania",
                          "30" = "Togo",
                          "31" = "Tunisia",
                          "32" = "Uganda",
                          "33" = "Zambia",
                          "34" = "Zimbabwe"))

afrobarometer_w7 %<>%
  mutate(corr_pres = case_when(Q44A == 0 ~ 1, #none
                               Q44A == 1 ~ 2,
                               Q44A == 2 ~ 3,
                               Q44A == 3 ~ 4), #all of them
         corr_gov = case_when(Q44C == 0 ~ 1, #none
                              Q44C == 1 ~ 2,
                              Q44C == 2 ~ 3,
                              Q44C == 3 ~ 4), #all of them
         corr_jud = case_when(Q44F == 0 ~ 1, #none
                              Q44F == 1 ~ 2,
                              Q44F == 2 ~ 3,
                              Q44F == 3 ~ 4), #all of them
         fight_corr = case_when(Q56K == 1 ~ 1, #1 very badly
                                Q56K == 2 ~ 2,
                                Q56K == 3 ~ 3,
                                Q56K == 4 ~ 4), #4 very well
         corr_leaders = case_when(Q44B == 0 ~ 1, #none of them
                                  Q44B == 1 ~ 2,
                                  Q44B == 2 ~ 3,
                                  Q44B == 3 ~ 4)) %>% # all of them
  purrr::modify_at(c('corr_pres', 'corr_gov', 'corr_jud', "fight_corr", 
                     "corr_leaders"), factor) %>%
  select(country, year, corr_pres, corr_gov, corr_jud, fight_corr, corr_leaders, survey) 

```

Merge all databases

```{r}
afrobarometer_final <- full_join(afrobarometer_w1, afrobarometer_w2)
afrobarometer_final <- full_join(afrobarometer_final, afrobarometer_w3)
afrobarometer_final <- full_join(afrobarometer_final, afrobarometer_w4)
afrobarometer_final <- full_join(afrobarometer_final, afrobarometer_w5)
afrobarometer_final <- full_join(afrobarometer_final, afrobarometer_w6)
afrobarometer_final <- full_join(afrobarometer_final, afrobarometer_w7)

# Convert some factors to numeric
afrobarometer_final %<>% mutate_at(c('year', 'fight_corr',
                                      'corr_leaders', 'corr_pres', 
                                      'corr_gov', 'corr_jud'), as.numeric)
```

## Arab Barometer

### Wave 1

```{r}
arab_barometer_w1 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/arab-barometer/AB_Wave_I_2006-2009.dta")

#Keep specific variables
arab_barometer_w1  %<>% select(country, q253, q2011, q2012, q254) %>%
  rename(widespread_corr = q253,
         conf_gov = q2011,
         conf_just = q2012,
         fight_corr = q254)

arab_barometer_w1 %<>% mutate(across(, ~as.numeric(.)))

# Widespread corruption
# 1 hardly anyone 2 not a lot of officials 3 most officials 4 almost everyone
table(arab_barometer_w1$widespread_corr)
arab_barometer_w1 %<>% mutate(widespread_corr = 
                             replace(widespread_corr, 
                                     widespread_corr == 98 | widespread_corr== 99, NA))

# Confidence in government
#1 a great deal 2 quite a lot 3 not very much 4 none at all
table(arab_barometer_w1$conf_gov)
arab_barometer_w1$conf_gov <- recode(arab_barometer_w1$conf_gov,
                                      "4 " = 1,
                                      "3" = 2,
                                      "2" = 3,
                                      "1" = 4)
arab_barometer_w1 %<>% mutate(conf_gov = 
                             replace(conf_gov, 
                                     conf_gov == 98 | conf_gov== 99, NA))

# Confidence courts
#1 a great deal 2 quite a lot 3 not very much 4 none at all
table(arab_barometer_w1$conf_just)
arab_barometer_w1$conf_just <- recode(arab_barometer_w1$conf_just,
                                      "4 " = 1,
                                      "3" = 2,
                                      "2" = 3,
                                      "1" = 4)
arab_barometer_w1 %<>% mutate(conf_just = 
                             replace(conf_just, 
                                     conf_just == 98 | conf_just == 99, NA))

# Fight corruption
# 1 to a large extent 2 to a medium 3 small 4 not at all
table(arab_barometer_w1$fight_corr)
arab_barometer_w1$fight_corr <- recode(arab_barometer_w1$fight_corr,
                                      "4 " = 1,
                                      "3" = 2,
                                      "2" = 3,
                                      "1" = 4)
arab_barometer_w1 %<>% mutate(fight_corr = 
                             replace(fight_corr, fight_corr == 97 |
                                     fight_corr == 98 | fight_corr == 99, NA))


arab_barometer_w1$country[arab_barometer_w1$country == "1"] <- "Jordan"
arab_barometer_w1$country[arab_barometer_w1$country == "2"] <- "Palestine" 
arab_barometer_w1$country[arab_barometer_w1$country == "3"] <- "Algeria"
arab_barometer_w1$country[arab_barometer_w1$country == "4"] <- "Morocco" 
arab_barometer_w1$country[arab_barometer_w1$country == "5"] <- "Kuwait" 
arab_barometer_w1$country[arab_barometer_w1$country == "6"] <- "Lebanon" 
arab_barometer_w1$country[arab_barometer_w1$country == "7"] <- "Yemen"
arab_barometer_w1$country[arab_barometer_w1$country == "8"] <- "Bahrain"

arab_barometer_w1$year <- 0
arab_barometer_w1$year[arab_barometer_w1$country == "Algeria"] <- "2006"
arab_barometer_w1$year[arab_barometer_w1$country == "Bahrain"] <- "2009"
arab_barometer_w1$year[arab_barometer_w1$country == "Jordan"] <- "2006"
arab_barometer_w1$year[arab_barometer_w1$country == "Lebanon"] <- "2006"
arab_barometer_w1$year[arab_barometer_w1$country == "Morocco"] <- "2007"
arab_barometer_w1$year[arab_barometer_w1$country == "Palestine"] <- "2006"
arab_barometer_w1$year[arab_barometer_w1$country == "Yemen"] <- "2007"
table(arab_barometer_w1$year)

arab_barometer_w1$year <- as.numeric(arab_barometer_w1$year)
table(arab_barometer_w1$country, arab_barometer_w1$year)

arab_barometer_w1 %<>%
purrr::modify_at(c("widespread_corr", "fight_corr", "conf_gov", "conf_just"), factor)
```

### Wave 2

```{r}
arab_barometer_w2 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/arab-barometer/AB_Wave_II_2010-2011.dta")

arab_barometer_w2$year <- 0
arab_barometer_w2$country <- as.numeric(arab_barometer_w2$country)

arab_barometer_w2$year[arab_barometer_w2$country == "1"] <- "2011"
arab_barometer_w2$year[arab_barometer_w2$country == "5"] <- "2011"
arab_barometer_w2$year[arab_barometer_w2$country == "7"] <- "2011"
arab_barometer_w2$year[arab_barometer_w2$country == "8"] <- "2010"
arab_barometer_w2$year[arab_barometer_w2$country == "10"] <- "2010"
arab_barometer_w2$year[arab_barometer_w2$country == "15"] <- "2010"
arab_barometer_w2$year[arab_barometer_w2$country == "17"] <- "2011"
arab_barometer_w2$year[arab_barometer_w2$country == "19"] <- "2010"
arab_barometer_w2$year[arab_barometer_w2$country == "21"] <- "2011"
arab_barometer_w2$year[arab_barometer_w2$country == "22"] <- "2011"

arab_barometer_w2$country[arab_barometer_w2$country == "1"] <- "Algeria"
arab_barometer_w2$country[arab_barometer_w2$country == "5"] <- "Egypt"
arab_barometer_w2$country[arab_barometer_w2$country == "7"] <- "Iraq"
arab_barometer_w2$country[arab_barometer_w2$country == "8"] <- "Jordan"
arab_barometer_w2$country[arab_barometer_w2$country == "10"] <- "Lebanon"
arab_barometer_w2$country[arab_barometer_w2$country == "15"] <- "Palestine"
arab_barometer_w2$country[arab_barometer_w2$country == "17"] <- "Saudi Arabia"
arab_barometer_w2$country[arab_barometer_w2$country == "19"] <- "Sudan"
arab_barometer_w2$country[arab_barometer_w2$country == "21"] <- "Tunisia"
arab_barometer_w2$country[arab_barometer_w2$country == "22"] <- "Yemen"

arab_barometer_w2 %<>%
  mutate(sat_dem = case_when(q513 == 1 ~ 1,
                             q513 == 2 ~ 1,
                             q513 == 3 ~ 1,
                             q513 == 4 ~ 2,
                             q513 == 5 ~ 2,
                             q513 == 6 ~ 3,
                             q513 == 7 ~ 3,
                             q513 == 8 ~ 4,
                             q513 == 9 ~ 4,
                             q513 == 10 ~ 4),
         fight_corr = case_when(q211 == 4 ~ 1,
                                q211 == 3 ~ 2,
                                q211 == 2 ~ 3,
                                q211 == 1 ~ 4),
         conf_gov = case_when(q2011 == 4 ~ 1,
                              q2011 == 3 ~ 2,
                              q2011 == 2 ~ 3,
                              q2011 == 1 ~ 4),
         conf_just = case_when(q2012 == 4 ~ 1,
                               q2012 == 3 ~ 2,
                               q2012 == 2 ~ 3,
                               q2012 == 1 ~ 4)) %>%
  purrr::modify_at(c("sat_dem", "fight_corr", "conf_gov", "conf_just"), factor) %>%
  select(country, year, sat_dem, fight_corr, conf_gov, conf_just) 
```

### Wave 3

```{r}
arab_barometer_w3 <- read_sav("data/arab-barometer/ABIII_English.sav")

arab_barometer_w3$year <- 0
arab_barometer_w3$country <- as.numeric(arab_barometer_w3$country)

arab_barometer_w3$country[arab_barometer_w3$country == "1"] <- "Algeria"
arab_barometer_w3$country[arab_barometer_w3$country == "5"] <- "Egypt"
arab_barometer_w3$country[arab_barometer_w3$country == "7"] <- "Iraq"
arab_barometer_w3$country[arab_barometer_w3$country == "8"] <- "Jordan"
arab_barometer_w3$country[arab_barometer_w3$country == "9"] <- "Kuwait"
arab_barometer_w3$country[arab_barometer_w3$country == "10"] <- "Lebanon"
arab_barometer_w3$country[arab_barometer_w3$country == "11"] <- "Libya"
arab_barometer_w3$country[arab_barometer_w3$country == "13"] <- "Morocco"
arab_barometer_w3$country[arab_barometer_w3$country == "15"] <- "Palestine"
arab_barometer_w3$country[arab_barometer_w3$country == "19"] <- "Sudan"
arab_barometer_w3$country[arab_barometer_w3$country == "21"] <- "Tunisia"
arab_barometer_w3$country[arab_barometer_w3$country == "22"] <- "Yemen"

arab_barometer_w3$year[arab_barometer_w3$country == "Algeria"] <- "2013"
arab_barometer_w3$year[arab_barometer_w3$country == "Egypt"] <- "2013"
arab_barometer_w3$year[arab_barometer_w3$country == "Iraq"] <- "2013"
arab_barometer_w3$year[arab_barometer_w3$country == "Jordan"] <- "2012"
arab_barometer_w3$year[arab_barometer_w3$country == "Kuwait"] <- "2014"
arab_barometer_w3$year[arab_barometer_w3$country == "Lebanon"] <- "2013"
arab_barometer_w3$year[arab_barometer_w3$country == "Libya"] <- "2014"
arab_barometer_w3$year[arab_barometer_w3$country == "Morocco"] <- "2013"
arab_barometer_w3$year[arab_barometer_w3$country == "Palestine"] <- "2012"
arab_barometer_w3$year[arab_barometer_w3$country == "Sudan"] <- "2013"
arab_barometer_w3$year[arab_barometer_w3$country == "Tunisia"] <- "2013"
arab_barometer_w3$year[arab_barometer_w3$country == "Yemen"] <- "2013"

arab_barometer_w3 %<>%
  mutate(sat_dem = case_when(q513 == 1 ~ 1,
                             q513 == 2 ~ 1,
                             q513 == 3 ~ 1,
                             q513 == 4 ~ 2,
                             q513 == 5 ~ 2,
                             q513 == 6 ~ 3,
                             q513 == 7 ~ 3,
                             q513 == 8 ~ 4,
                             q513 == 9 ~ 4,
                             q513 == 10 ~ 4),
         fight_corr = case_when(q211 == 4 ~ 1,
                                q211 == 3 ~ 2,
                                q211 == 2 ~ 3,
                                q211 == 1 ~ 4),
         conf_gov = case_when(q2011 == 4 ~ 1,
                              q2011 == 3 ~ 2,
                              q2011 == 2 ~ 3,
                              q2011 == 1 ~ 4)) %>%
  purrr::modify_at(c("sat_dem", "fight_corr", "conf_gov"), factor) %>%
  select(country, year, sat_dem, fight_corr, conf_gov) 
```

### Wave 4

```{r}
arab_barometer_w4 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/arab-barometer/AB_Wave_IV_2014-2017.dta") 

arab_barometer_w4$year <- 0
arab_barometer_w4$country <- as.numeric(arab_barometer_w4$country)

arab_barometer_w4$country[arab_barometer_w4$country == "1"] <- "Algeria"
arab_barometer_w4$country[arab_barometer_w4$country == "5"] <- "Egypt"
arab_barometer_w4$country[arab_barometer_w4$country == "8"] <- "Jordan"
arab_barometer_w4$country[arab_barometer_w4$country == "10"] <- "Lebanon"
arab_barometer_w4$country[arab_barometer_w4$country == "13"] <- "Morocco"
arab_barometer_w4$country[arab_barometer_w4$country == "15"] <- "Palestine"
arab_barometer_w4$country[arab_barometer_w4$country == "21"] <- "Tunisia"

arab_barometer_w4$year[arab_barometer_w4$country == "Algeria"] <- "2016"
arab_barometer_w4$year[arab_barometer_w4$country == "Egypt"] <- "2016"
arab_barometer_w4$year[arab_barometer_w4$country == "Jordan"] <- "2016"
arab_barometer_w4$year[arab_barometer_w4$country == "Lebanon"] <- "2016"
arab_barometer_w4$year[arab_barometer_w4$country == "Morocco"] <- "2016"
arab_barometer_w4$year[arab_barometer_w4$country == "Palestine"] <- "2016"
arab_barometer_w4$year[arab_barometer_w4$country == "Tunisia"] <- "2016"

arab_barometer_w4 %<>%
  mutate(sat_dem = case_when(q513 == 1 ~ 1,
                             q513 == 2 ~ 1,
                             q513 == 3 ~ 1,
                             q513 == 4 ~ 2,
                             q513 == 5 ~ 2,
                             q513 == 6 ~ 3,
                             q513 == 7 ~ 3,
                             q513 == 8 ~ 4,
                             q513 == 9 ~ 4,
                             q513 == 10 ~ 4),
         fight_corr = case_when(q211 == 4 ~ 1,
                                q211 == 3 ~ 2,
                                q211 == 2 ~ 3,
                                q211 == 1 ~ 4),
         conf_gov = case_when(q2011 == 4 ~ 1,
                              q2011 == 3 ~ 2,
                              q2011 == 2 ~ 3,
                              q2011 == 1 ~ 4),
         conf_just = case_when(q2012 == 4 ~ 1,
                               q2012 == 3 ~ 2,
                               q2012 == 2 ~ 3,
                               q2012 == 1 ~ 4)) %>%
  purrr::modify_at(c("sat_dem", "fight_corr", "conf_gov", "conf_just"), factor) %>%
  select(country, year, sat_dem, fight_corr, conf_gov, conf_just) 
```

### Wave 5

```{r}
arab_barometer_w5 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/arab-barometer/AB_Wave_V_2018-2019.dta") 

arab_barometer_w5$year <- 0
arab_barometer_w5$country <- as.numeric(arab_barometer_w5$country)

arab_barometer_w5$country <- recode(arab_barometer_w5$country,
                             "1" = "Algeria",
                             "5" = "Egypt",
                             "7" = "Iraq",
                             "8" = "Jordan",
                             "9" = "Kuwait",
                             "10" = "Lebanon",
                             "11" = "Libya",
                             "13" = "Morocco",
                             "15" = "Palestine",
                             "19" = "Sudan",
                             "21" = "Tunisia",
                             "22" = "Yemen")

arab_barometer_w5$year[arab_barometer_w5$country == "Algeria"] <- "2019"
arab_barometer_w5$year[arab_barometer_w5$country == "Egypt"] <- "2018"
arab_barometer_w5$year[arab_barometer_w5$country == "Iraq"] <- "2019"
arab_barometer_w5$year[arab_barometer_w5$country == "Jordan"] <- "2018"
arab_barometer_w5$year[arab_barometer_w5$country == "Kuwait"] <- "2019"
arab_barometer_w5$year[arab_barometer_w5$country == "Lebanon"] <- "2018"
arab_barometer_w5$year[arab_barometer_w5$country == "Libya"] <- "2019"
arab_barometer_w5$year[arab_barometer_w5$country == "Morocco"] <- "2018"
arab_barometer_w5$year[arab_barometer_w5$country == "Palestine"] <- "2018"
arab_barometer_w5$year[arab_barometer_w5$country == "Sudan"] <- "2018"
arab_barometer_w5$year[arab_barometer_w5$country == "Tunisia"] <- "2018"
arab_barometer_w5$year[arab_barometer_w5$country == "Yemen"] <- "2018"

arab_barometer_w5 %<>%
  mutate(sat_dem = case_when(Q513 == 1 ~ 1,
                             Q513 == 2 ~ 1,
                             Q513 == 3 ~ 1,
                             Q513 == 4 ~ 2,
                             Q513 == 5 ~ 2,
                             Q513 == 6 ~ 3,
                             Q513 == 7 ~ 3,
                             Q513 == 8 ~ 4,
                             Q513 == 9 ~ 4,
                             Q513 == 10 ~ 4),
         fight_corr = case_when(Q211 == 4 ~ 1,
                                Q211 == 3 ~ 2,
                                Q211 == 2 ~ 3,
                                Q211 == 1 ~ 4),
         conf_gov = case_when(Q201A_1 == 4 ~ 1,
                              Q201A_1 == 3 ~ 2,
                              Q201A_1 == 2 ~ 3,
                              Q201A_1 == 1 ~ 4),
         conf_just = case_when(Q201A_2 == 4 ~ 1,
                               Q201A_2 == 3 ~ 2,
                               Q201A_2 == 2 ~ 3,
                               Q201A_2 == 1 ~ 4),
         extent_corr = case_when(Q210 == 4 ~ 1,
                                 Q210 == 3 ~ 2,
                                 Q210 == 2 ~ 3,
                                 Q210 == 1 ~ 4),
         groups_corruption = case_when(Q211A == 1 ~ 1,
                                       Q211A == 2 ~ 2,
                                       Q211A == 3 ~ 3,
                                       Q211A == 4 ~ 4,)) %>%
  purrr::modify_at(c("sat_dem", "fight_corr", "conf_gov", "conf_just", "extent_corr",
                     "groups_corruption"), factor) %>%
  select(country, year, sat_dem, fight_corr, conf_gov, conf_just, extent_corr,
         groups_corruption) 
```

### Wave 6

```{r}
arab_barometer_w6_p1 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/arab-barometer/AB_Wave_VI_P1-2020.dta")
arab_barometer_w6_p2 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/arab-barometer/AB_Wave_VI_P2-2020.dta")
arab_barometer_w6_p3 <- read_dta("~/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/arab-barometer/AB_Wave_VI_P3-2021.dta")

# Select specific columns
arab_barometer_w6_p1 <- select(arab_barometer_w6_p1, 
                               c(COUNTRY, DATE, Q201A_1, Q201A_2, Q210, Q211, Q204A_3))
arab_barometer_w6_p2 <- select(arab_barometer_w6_p2, 
                               c(COUNTRY, DATE, Q201A_1, Q201A_2, Q210))
arab_barometer_w6_p3 <- select(arab_barometer_w6_p3, 
                               c(COUNTRY, DATE, Q201A_1, Q201A_2, Q210, Q211, Q204A_3))

arab_barometer_w6_p2$Q211 <- NA
arab_barometer_w6_p2$Q204A_3 <- NA
arab_barometer_w6_p3$DATE <- as.Date(arab_barometer_w6_p3$DATE)

arab_barometer_w6 <- rbind(arab_barometer_w6_p1, arab_barometer_w6_p2)
arab_barometer_w6 <- bind_rows(arab_barometer_w6, arab_barometer_w6_p3)
names(arab_wave6)

arab_barometer_w6$COUNTRY <- as.numeric(arab_barometer_w6$COUNTRY)
arab_barometer_w6$year <- format(as.Date(arab_barometer_w6$DATE, format="%Y-%m-%d"),"%Y")

arab_barometer_w6$country <- recode(arab_barometer_w6$COUNTRY,
                             "1" = "Algeria",
                             "7" = "Iraq",
                             "8" = "Jordan",
                             "10" = "Lebanon",
                             "11" = "Libya",
                             "13" = "Morocco",
                             "21" = "Tunisia")


arab_barometer_w6 %<>%
  mutate(sat_dem = case_when(Q204A_3 == 4 ~ 1,
                             Q204A_3 == 3 ~ 1,
                             Q204A_3 == 2 ~ 1,
                             Q204A_3 == 1 ~ 2),
         fight_corr = case_when(Q211 == 4 ~ 1,
                                Q211 == 3 ~ 2,
                                Q211 == 2 ~ 3,
                                Q211 == 1 ~ 4),
         conf_gov = case_when(Q201A_1 == 4 ~ 1,
                              Q201A_1 == 3 ~ 2,
                              Q201A_1 == 2 ~ 3,
                              Q201A_1 == 1 ~ 4),
         conf_just = case_when(Q201A_2 == 4 ~ 1,
                               Q201A_2 == 3 ~ 2,
                               Q201A_2 == 2 ~ 3,
                               Q201A_2 == 1 ~ 4),
         extent_corr = case_when(Q210 == 4 ~ 1,
                                 Q210 == 3 ~ 2,
                                 Q210 == 2 ~ 3,
                                 Q210 == 1 ~ 4)) %>%
  purrr::modify_at(c("sat_dem", "fight_corr", "conf_gov", "conf_just", "extent_corr"), 
                   factor) %>%
  select(country, year, sat_dem, fight_corr, conf_gov, conf_just, extent_corr) 
```

Merge all databases

```{r}
arab_barometer_w1$year <- as.numeric(arab_barometer_w1$year)
arab_barometer_w2$year <- as.numeric(arab_barometer_w2$year)
arab_barometer_w3$year <- as.numeric(arab_barometer_w3$year)
arab_barometer_w4$year <- as.numeric(arab_barometer_w4$year)
arab_barometer_w5$year <- as.numeric(arab_barometer_w5$year)
arab_barometer_w6$year <- as.numeric(arab_barometer_w6$year)

arab_barometer_w1$survey <- 'arab_barometer_w1'
arab_barometer_w2$survey <- 'arab_barometer_w2'
arab_barometer_w3$survey <- 'arab_barometer_w3'
arab_barometer_w4$survey <- 'arab_barometer_w4'
arab_barometer_w5$survey <- 'arab_barometer_w5'
arab_barometer_w6$survey <- 'arab_barometer_w6'

arab_barometer_final <- full_join(arab_barometer_w1, arab_barometer_w2)
arab_barometer_final <- full_join(arab_barometer_final, arab_barometer_w3)
arab_barometer_final <- full_join(arab_barometer_final, arab_barometer_w4)
arab_barometer_final <- full_join(arab_barometer_final, arab_barometer_w5)
arab_barometer_final <- full_join(arab_barometer_final, arab_barometer_w6)

# Convert some factors to numeric
arab_barometer_final %<>% mutate_at(c('widespread_corr', 'conf_gov',
                                      'conf_just', 'fight_corr', 
                                      'year', 'sat_dem', 'extent_corr',
                                      'groups_corruption'), as.numeric)
```

## Asiabarometer 

### Wave 1

```{r}
asiabarometer_w1 <- read_sav("data/asia-barometer/W1 Merged Data/Wave.1_Data/Merge/Wave1_20170906.sav")

asiabarometer_w1 %<>%
  mutate(country = case_when(country == 1 ~ 'Japan',
                             country == 2 ~ 'Hong Kong',
                             country == 3 ~ 'Korea',
                             country == 4 ~ 'China',
                             country == 5 ~ 'Mongolia',
                             country == 6 ~ 'Philippines',
                             country == 7 ~ 'Taiwan',
                             country == 8 ~ 'Thailand'))

names(asiabarometer_w1)

asiabarometer_w1$survey <- 'asiabarometer_w1'

asiabarometer_w1 %<>%
  mutate(sat_dem = case_when(q098 == 4 ~ 1, #not all satisfied
                             q098 == 3 ~ 2,
                             q098 == 2 ~ 3,
                             q098 == 1 ~ 4), #very satisfied 
         evol_corr = case_when(q108 == 5 ~ 1, #much worse
                               q108 == 4 ~ 2,
                               q108 == 3 ~ 3,
                               q108 == 2 ~ 4,
                               q108 == 1 ~ 5),#much better
         conf_gov = case_when(q008 == 4 ~ 1, #not at all
                              q008 == 3 ~ 2,
                              q008 == 2 ~ 3,
                              q008 == 1 ~ 4),
         conf_just = case_when(q007 == 4 ~ 1, #not at all
                               q007 == 3 ~ 2,
                               q007 == 2 ~ 3,
                               q007 == 1 ~ 4)) %>%  #a great deal
  rename(extent_corr = q141,
         year = yrsurvey) %>% # from hardly anyone to almost everyone
  purrr::modify_at(c("sat_dem", "conf_gov", "conf_just", "evol_corr"), 
                   factor) %>%
  select(country, year, sat_dem, conf_gov, conf_just, evol_corr,survey) 
```

### Wave 2

```{r}
asiabarometer_w2 <- read_sav("data/asia-barometer/W2 Merged Data/2w-3rd_release_all/merge/Wave2_20170724.sav")

asiabarometer_w2 %<>%
  mutate(country = case_when(country == 1 ~ 'Japan',
                             country == 2 ~ 'Hong Kong',
                             country == 3 ~ 'Korea',
                             country == 4 ~ 'China',
                             country == 5 ~ 'Mongolia',
                             country == 6 ~ 'Philippines',
                             country == 7 ~ 'Taiwan',
                             country == 8 ~ 'Thailand',
                             country == 9 ~ 'Indonesia',
                             country == 10 ~ 'Singapore',
                             country == 11 ~ 'Vietnam',
                             country == 12 ~ 'Cambodia',
                             country == 13 ~ 'Malaysia'))

asiabarometer_w2$year <- 0

asiabarometer_w2$year[asiabarometer_w2$country == "Japan"] <- "2007"
asiabarometer_w2$year[asiabarometer_w2$country == "Hong Kong"] <- "2007"
asiabarometer_w2$year[asiabarometer_w2$country == 'Korea'] <- "2006"
asiabarometer_w2$year[asiabarometer_w2$country == 'China'] <- "2008"                      
asiabarometer_w2$year[asiabarometer_w2$country == 'Mongolia'] <- "2006"
asiabarometer_w2$year[asiabarometer_w2$country == 'Philippines'] <- "2005"
asiabarometer_w2$year[asiabarometer_w2$country == 'Taiwan'] <- "2006"
asiabarometer_w2$year[asiabarometer_w2$country == 'Thailand'] <- "2006"
asiabarometer_w2$year[asiabarometer_w2$country == 'Indonesia'] <- "2006"
asiabarometer_w2$year[asiabarometer_w2$country ==  'Singapore'] <- "2006"
asiabarometer_w2$year[asiabarometer_w2$country ==  'Vietnam'] <- "2005"
asiabarometer_w2$year[asiabarometer_w2$country ==  'Cambodia'] <- "2008"
asiabarometer_w2$year[asiabarometer_w2$country ==  'Malaysia'] <- "2007"

asiabarometer_w2$survey <- 'asiabarometer_w2'

asiabarometer_w2 %<>%
  mutate(sat_dem = case_when(q93 == 1 ~ 1, #not all satisfied
                             q93 == 2 ~ 2,
                             q93 == 3 ~ 3,
                             q93 == 4 ~ 4), #very satisfied 
         extent_corr = case_when(q118 == 4 ~ 1, #hardy anyone is involved
                                 q118 == 3 ~ 2,
                                 q118 == 2 ~ 3,
                                 q118 == 1 ~ 4), #almost everyone is corrupt
         evol_corr = case_when(q108 == 5 ~ 1, #much worse
                               q108 == 4 ~ 2,
                               q108 == 3 ~ 3,
                               q108 == 2 ~ 4,
                               q108 == 1 ~ 5),#much better
         fight_corr = case_when(q120 == 4 ~ 1, #doing nothing
                                q120 == 3 ~ 2,
                                q120 == 2 ~ 3,
                                q120 == 1 ~ 4, #doing its best
                                q120 == 0 ~ 4), #doing this effectively
         conf_gov = case_when(q9 == 1 ~ 1, #not at all
                              q9 == 2 ~ 2,
                              q9 == 3 ~ 3,
                              q9 == 4 ~ 4),
         conf_just = case_when(q8 == 1 ~ 1, #not at all
                               q8 == 2 ~ 2,
                               q8 == 3 ~ 3,
                               q8 == 4 ~ 4)) %>%  #a great deal
  purrr::modify_at(c("sat_dem", 'extent_corr', 'evol_corr',  'fight_corr', 'conf_gov',
                     'conf_just'), 
                   factor) %>%
  select(country, year, sat_dem, extent_corr, conf_gov, conf_just, evol_corr, survey,
         fight_corr) 

```

### Wave 3

```{r}
asiabarometer_w3 <- read_sav("data/asia-barometer/ABS3w.0.Merged/ABS3 merge20210506.sav")

asiabarometer_w3 %<>%
  mutate(country = case_when(country == 1 ~ 'Japan',
                             country == 2 ~ 'Hong Kong',
                             country == 3 ~ 'Korea',
                             country == 4 ~ 'China',
                             country == 5 ~ 'Mongolia',
                             country == 6 ~ 'Philippines',
                             country == 7 ~ 'Taiwan',
                             country == 8 ~ 'Thailand',
                             country == 9 ~ 'Indonesia',
                             country == 10 ~ 'Singapore',
                             country == 11 ~ 'Vietnam',
                             country == 12 ~ 'Cambodia',
                             country == 13 ~ 'Malaysia'))

asiabarometer_w3$year <- 0

asiabarometer_w3$year[asiabarometer_w3$country == "Japan"] <- "2011"
asiabarometer_w3$year[asiabarometer_w3$country == "Hong Kong"] <- "2012"
asiabarometer_w3$year[asiabarometer_w3$country == 'Korea'] <- "2011"
asiabarometer_w3$year[asiabarometer_w3$country == 'China'] <- "2011"                      
asiabarometer_w3$year[asiabarometer_w3$country == 'Mongolia'] <- "2010"
asiabarometer_w3$year[asiabarometer_w3$country == 'Philippines'] <- "2010"
asiabarometer_w3$year[asiabarometer_w3$country == 'Taiwan'] <- "2010"
asiabarometer_w3$year[asiabarometer_w3$country == 'Thailand'] <- "2010"
asiabarometer_w3$year[asiabarometer_w3$country == 'Indonesia'] <- "2011"
asiabarometer_w3$year[asiabarometer_w3$country ==  'Singapore'] <- "2010"
asiabarometer_w3$year[asiabarometer_w3$country ==  'Vietnam'] <- "2010"
asiabarometer_w3$year[asiabarometer_w3$country ==  'Cambodia'] <- "2012"
asiabarometer_w3$year[asiabarometer_w3$country ==  'Malaysia'] <- "2010"

asiabarometer_w3$survey <- 'asiabarometer_w3'

asiabarometer_w3 %<>%
  mutate(sat_dem = case_when(q89 == 4 ~ 1, #not all satisfied
                             q89 == 3 ~ 2,
                             q89 == 2 ~ 3,
                             q89 == 1 ~ 4), #very satisfied 
         extent_corr = case_when(q117 == 1 ~ 1, #hardy anyone is involved
                                 q117 == 2 ~ 2,
                                 q117 == 3 ~ 3,
                                 q117 == 4 ~ 4), #almost everyone is corrupt
         fight_corr = case_when(q118 == 4 ~ 1, #doing nothing
                                q118 == 3 ~ 2,
                                q118 == 2 ~ 3,
                                q118 == 1 ~ 4), #doing its best
         conf_gov = case_when(q9 == 1 ~ 1, #not at all
                              q9 == 2 ~ 2,
                              q9 == 3 ~ 3,
                              q9 == 4 ~ 4),
         conf_just = case_when(q8 == 1 ~ 1, #not at all
                               q8 == 2 ~ 2,
                               q8 == 3 ~ 3,
                               q8 == 4 ~ 4)) %>%  #a great deal
  purrr::modify_at(c("sat_dem", 'extent_corr',  'fight_corr', 'conf_gov',
                     'conf_just'), 
                   factor) %>%
  select(country, year, sat_dem, extent_corr, conf_gov, conf_just, survey,
         fight_corr) 
```

### Wave 4

```{r}
asiabarometer_w4 <- read_dta("data/asia-barometer/W4 Merged Data/W4_v15_merged20181211_release.dta")

asiabarometer_w4 %<>%
  mutate(country = case_when(country == 1 ~ 'Japan',
                             country == 2 ~ 'Hong Kong',
                             country == 3 ~ 'Korea',
                             country == 4 ~ 'China',
                             country == 5 ~ 'Mongolia',
                             country == 6 ~ 'Philippines',
                             country == 7 ~ 'Taiwan',
                             country == 8 ~ 'Thailand',
                             country == 9 ~ 'Indonesia',
                             country == 10 ~ 'Singapore',
                             country == 11 ~ 'Vietnam',
                             country == 12 ~ 'Cambodia',
                             country == 13 ~ 'Malaysia',
                             country == 14 ~ 'Myanmar'))

asiabarometer_w4$survey <- 'asiabarometer_w4'

asiabarometer_w4 %<>%
  mutate(sat_dem = case_when(q92 == 4 ~ 1, #not all satisfied
                             q92 == 3 ~ 2,
                             q92 == 2 ~ 3,
                             q92 == 1 ~ 4), #very satisfied 
         extent_corr = case_when(q134 == 1 ~ 1, #hardy anyone is involved
                                 q134 == 2 ~ 2,
                                 q134 == 3 ~ 3,
                                 q134 == 4 ~ 4), #almost everyone is corrupt
         fight_corr = case_when(q135 == 4 ~ 1, #doing nothing
                                q135 == 3 ~ 2,
                                q135 == 2 ~ 3,
                                q135 == 1 ~ 4), #doing its best
         conf_gov = case_when(q119 == 1 ~ 1, #none
                              q119 == 2 ~ 2,
                              q119 == 3 ~ 3,
                              q119 == 4 ~ 4), #all of them
         conf_just = case_when(q122 == 1 ~ 1, #none
                               q122 == 2 ~ 2,
                               q122 == 3 ~ 3,
                               q122 == 4 ~ 4)) %>%  #all of them
  purrr::modify_at(c("sat_dem", 'extent_corr',  'fight_corr', 'conf_gov',
                     'conf_just'), 
                   factor) %>%
  select(country, year, sat_dem, extent_corr, conf_gov, conf_just, survey,
         fight_corr) 
```

Join All Asiabarometer

```{r}
asiabarometer_w1$year <- as.numeric(asiabarometer_w1$year)
asiabarometer_w2$year <- as.numeric(asiabarometer_w2$year)
asiabarometer_w3$year <- as.numeric(asiabarometer_w3$year)
asiabarometer_w4$year <- as.numeric(asiabarometer_w4$year)

asiabarometer_final <- full_join(asiabarometer_w1, asiabarometer_w2)
asiabarometer_final <- full_join(asiabarometer_final, asiabarometer_w3)
asiabarometer_final <- full_join(asiabarometer_final, asiabarometer_w4)

#Convert some factors to numeric
names(asiabarometer_final)
asiabarometer_final %<>% mutate_at(c('year', 'sat_dem', 'conf_gov', 
                                     'conf_just', 'evol_corr', 'extent_corr',
                                     'fight_corr'), as.numeric)
```

## World Values Survey

```{r}
load("~/Documents/PhD/1_Research/transitional-justice/Data/Data 2022/TJ R Project/Data bases/WVS/WVS_TimeSeries_1981_2022_Rdata_v3_0.rdata")

wvs_raw <- WVS_TimeSeries_1981_2022_spss_v3_0
rm(WVS_TimeSeries_1981_2022_spss_v3_0)

# Add country names and year
wvs_raw$country <- NA
wvs_raw$year <- wvs_raw$S020
wvs_raw$ccode <- wvs_raw$COW_NUM

library(countrycode)
wvs_raw$country <- NA
wvs_raw$year <- wvs_raw$S020
wvs_raw$ccode <- wvs_raw$COW_NUM

wvs_raw$country <- countrycode(wvs_raw$COUNTRY_ALPHA, origin = "iso3c",
                             destination = "country.name", warn = TRUE)

wvs_raw <- relocate(wvs_raw, country)
```

Select only variables that matter

```{r}
wvs$survey <- 'wvs'

wvs %<>%
  mutate(sat_dem = case_when(E110 == 4 ~ 1, #not all satisfied
                             E110 == 3 ~ 2,
                             E110 == 2 ~ 3,
                             E110 == 1 ~ 4), #very satisfied 
         extent_corr = case_when(E196 == 1 ~ 1, # Almost no public officials engaged in it
                                 E196 == 2 ~ 2,
                                 E196 == 3 ~ 3,
                                 E196 == 4 ~ 4), #Almost all public officials
         conf_gov = case_when(E069_11 == 4 ~ 1, #None at all
                              E069_11 == 3 ~ 2,
                              E069_11 == 2 ~ 3,
                              E069_11 == 1 ~ 4), #A great deal
         conf_just = case_when(E069_17 == 4 ~ 1, #None at all
                               E069_17 == 3 ~ 2,
                               E069_17 == 2 ~ 3,
                               E069_17 == 1 ~ 4)) %>%  #A great deal
  purrr::modify_at(c("sat_dem", 'extent_corr', 'conf_gov', 'conf_just'), 
                   factor) %>%
  select(country, year, sat_dem, extent_corr, conf_gov, conf_just, survey) 


#Convert some factors to numeric
names(wvs)
wvs %<>% mutate_at(c('year', 'sat_dem', 'extent_corr', 'conf_gov', 
                     'conf_just'), as.numeric)
```

## LAPOP

```{r}
lapop <- read_dta("data/lapop/lapop.dta")

lapop$country <- as.numeric(lapop$pais)

lapop %<>%
  mutate(country = recode(country,
                          "1" = "Mexico",
                          "2" = "Guatemala",
                          "3" = "El Salvador",
                          "4" = "Honduras",
                          "5" = "Nicaragua",
                          "6" = "Costa Rica",
                          "7" = "Panama",
                          "8" = "Colombia",
                          "9" = "Ecuador",
                          "10" = "Bolivia",
                          "11" = "Peru",
                          "12" = "Paraguay",
                          "13" = "Chile",
                          "14" = "Uruguay",
                          "15" = "Brazil",
                          "16" = "Venezuela",
                          "17" = "Argentina",
                          "21" = "Dominican Republic",
                          "22" = "Haiti",
                          "23" = "Jamaica",
                          "24" = "Guyana",
                          "25" = "Trinidad and Tobago",
                          "26" = "Belize",
                          "27" = "Surinam",
                          "28" = "Bahamas",
                          "29" = "Barbados",
                          "40" = "USA",
                          "41" = "Canada"))
lapop$survey <- 'lapop'

lapop %<>%
  mutate(sat_dem = case_when(pn4 == 4 ~ 1, #Muy insatisfecho(a)
                             pn4 == 3 ~ 2,
                             pn4 == 2 ~ 3,
                             pn4 == 1 ~ 4), #Muy satisfecho(a)
         extent_corr = case_when(pc2 == 10 ~ 1, # Muy honrados
                                 pc2 == 9 ~ 1,
                                 pc2 == 8 ~ 1,
                                 pc2 == 8 ~ 2,
                                 pc2 == 6 ~ 2,
                                 pc2 == 5 ~ 3,
                                 pc2 == 4 ~ 3,
                                 pc2 == 3 ~ 4,
                                 pc2 == 2 ~ 4,
                                 pc2 == 1 ~ 4), #Muy corruptos
         conf_gov = case_when(b14 == 1 ~ 1, #Nada
                              b14 == 2 ~ 1,
                              b14 == 3 ~ 2,
                              b14 == 4 ~ 2,
                              b14 == 5 ~ 3,
                              b14 == 6 ~ 4,
                              b14 == 7 ~ 4), #Mucho
         conf_just = case_when(b10a == 1 ~ 1, #None at all
                               b10a == 2 ~ 1,
                               b10a == 3 ~ 2,
                               b10a == 4 ~ 2,
                               b10a == 5 ~ 3,
                               b10a == 6 ~ 4,
                               b10a == 7 ~ 4)) %>%  #A great deal
  purrr::modify_at(c("sat_dem", 'extent_corr', 'conf_gov', 'conf_just'), 
                   factor) %>%
  select(country, year, sat_dem, extent_corr, conf_gov, conf_just, survey) 

#Convert some factors to numeric
names(lapop)
lapop %<>% mutate_at(c('year', 'sat_dem', 'extent_corr', 'conf_gov', 
                     'conf_just'), as.numeric)
```

## Latinobarometer

```{r}
# Set the range of years
years <- c(2010, 2011, 2013, 2015:2018, 2020)

# Create an empty list to store the data
latinobarometer <- list()

# Loop through the years
for (year in years) {
  
  # Load the data for the current year
  filename <- paste0("/Users/fran/Documents/PhD/1_Research/transitional-justice/tj-corruption-project/data/latino-barometer/", year, "_Latinobarometro_English.dta")
  data <- read_dta(filename)
  
  # Store the data in the list
  latinobarometer[[year]] <- data
}
```

## Join databases

```{r}
surveys_all <- full_join(afrobarometer_final, arab_barometer_final)
surveys_all <- full_join(surveys_all, asiabarometer_final)
surveys_all <- full_join(surveys_all, wvs)
surveys_all <- full_join(surveys_all, lapop)
```

### Modify database to long format

```{r}
surveys_long_raw <- surveys_all %>% 
  gather(attribute, response, -country, -year, -survey)

# Create a new variable "sample" using group_by and summarise
surveys_long <- surveys_long_raw %>%
  group_by(country, year, attribute, response, survey) %>%
  summarise(sample = n())

# Create a new variable "sample_survey" using group_by and summarise
surveys_long_sample_survey <- surveys_all %>%
  group_by(country, year) %>%
  summarise(sample_survey = n())

# Join the sample_survey variable to the original one
surveys_long %<>%
  left_join(surveys_long_sample_survey, by = c("country", "year")) %>%
  filter(!is.na(response))

# Create a new variable "proportion" by dividing the number of responses for each attribute by the sample size
surveys_long$response_prop <- surveys_long$sample / surveys_long$sample_survey

# Keep only 4 response alternative
surveys_long_filtered <- surveys_long %>%
  filter(response == 4)

# Save both long and filtered format
save(surveys_long, file = "surveys_long.RData")
save(surveys_long_filtered, file = "surveys_long_filtered.RData")
```
