---
title: "TJ R Project"
author: "Francisca Castro"
date: "4/28/2022"
output: html_document
---

# Packages Installation
```{r message=FALSE, warning=FALSE}
pacman::p_load(readxl, tidyverse, dplyr, readr, BBmisc, xlsx, haven,
               formattable, writexl, countrycode, panelView, countrycode)
```

# Load TJ data

```{r}
# Panel View - Figure 2 of manuscript
db_final <- read_excel("db_final_220527.xlsx")

# Subset inclusion_final_db == 1
db_subset <- db_final %>%
  filter(inclusion_final_db == 1)

# Use TJ_filtered instead but create a binary regime variable
tj_filtered$regime_binary <- NA

tj_filtered$regime_binary[tj_filtered$regime_polity5 == "democracy"] <- "partial_or_dem"
tj_filtered$regime_binary[tj_filtered$regime_polity5 == "partial democracy"] <- "partial_or_dem"

# Create figure
panel_figure_manuscript <- panelview(transition ~ treated, 
                                     data = tj_filtered,
                                     index = c("country", "year"), main = "",
                                     axis.lab.gap = c(2,0), xlab="", ylab="",
                                     legend.labs = c("Partial Democracy/Democracy", 
                                                     "TJ Implementations", 
                                                     "Non-democracy")) + 
  theme_minimal() +
  theme(legend.title = element_blank(), legend.position = c("bottom"),
        plot.title = element_text(hjust = 0.5))

tj_filtered <- subset(tj_filtered, country!= "Turkey")


panel_figure_manuscript


# Subset db_final to get a figure that fits into beamer (only for presentations)
tj_filtered_subset <- tj_filtered %>%
  filter(country %in% c("Argentina", "Bolivia", "Burkina Faso", "DR Congo",
                      "El Salvador", "Ethiopia", "Guinea", "Kenya", "Macedonia",
                      "Mozambique", "Niger", "Panama", "Romania", "Senegal",
                      "Tanzania", "Zimbabwe")) 

panel_figure2 <- panelview(transition ~ treated, data = tj_filtered_subset,
                       index = c("country", "year"), main = "",
                       axis.lab.gap = c(2,0), xlab="", ylab="",
           legend.labs = c("Partial Democracy/Democracy", 
                                                     "TJ Implementations", 
                                                     "Non-democracy")) +
   theme_minimal() +
   theme(legend.title = element_blank(),
         legend.position = c("bottom"),
         plot.title = element_text(hjust = 0.5))
panel_figure2
```

# Load TJ dataset
```{r}
tj <- read_excel("~/Documents/PhD/1_Research/9. Transitional justice/Data/Data 2022/tj_db_220425.xlsx")

table(tj$country)
```

# WVS

```{r}
load("~/Documents/PhD/1_Research/9. Transitional justice/Data/Data 2022/TJ R Project/Data bases/WVS/WVS_TimeSeries_1981_2022_Rdata_v3_0.rdata")

wvs_full <- WVS_TimeSeries_1981_2022_spss_v3_0
rm(WVS_TimeSeries_1981_2022_spss_v3_0)

head(wvs_full)
```
Add country names
```{r}
wvs_full$country <- NA
wvs_full$year <- wvs_full$S020
wvs_full$ccode <- wvs_full$COW_NUM

wvs_full$country <- countrycode(wvs_full$COUNTRY_ALPHA, origin = "iso3c",
                             destination = "country.name", warn = TRUE)

wvs_full <- relocate(wvs_full, country)
head(wvs_full)
```

Select only variables that matter
```{r}
wvs_filter <- wvs_full %>%
  select(c(country, year, ccode, COUNTRY_ALPHA, COW_ALPHA, 
           E196, E268, E269, E069_11, E069_17, E110))

rm(wvs_full)
head(wvs_filter)
```


Specific questions to keep
E196 - Extent of political corruption
How widespread do you think bride taking and corruption is in this country?
1  Almost no public officials engaged in it
2  A few are
3  Most are
4  Almost all public officials are engaged in it
-1  Don´t know
-2  No answer
-4  Not asked

E268 - Scale corruption in [my country] - pay a bribe, give a gift, do a favor to other to get things
1  There is no corruption in [my country]
2  2
3  3
4  4
5  5
6  6
7  7
8  8
9  9
10  There is abundant corruption in [my country]
-1  Don´t know
-2  No answer
-3  Not applicable
-4  Not asked
-5  Missing; Not available

E269 - Groups of people involved in corruption: State authorities
1  None of them
2  Few of them
3  Most of them
4  All of them
-1  Don´t know
-2  No answer
-4  Not asked
-5  Missing; Not available

E069_11 - Confidence: The Government
1  A great deal
2  Quite a lot
3  Not very much
4  None at all
-1  Don´t know
-2  No answer
-4  Not asked
-5  Missing; Unknown

E069_17 - Confidence: Justice System/Courts
1  A great deal
2  Quite a lot
3  Not very much
4  None at all
-1  Don´t know
-2  No answer
-4  Not asked
-5  Missing; Unknown

E110 - Satisfaction with the way democracy develops
1  Very satisfied
2  Rather satisfied
3  Not very satisfied
4  Not at all satisfied
-1  Don´t know
-2  No answer
-4  Not asked
-5  Missing; Unknown


```{r}
wvs_clean <- 
  wvs_filter %>% 
  mutate(E196 = replace(E196, E196 <= 0, NA),
         E268 = replace(E268, E268 <= 0, NA),
         E269 = replace(E269, E269 <= 0, NA),
         E069_11 = replace(E069_11, E069_11 <= 0, NA),
         E069_17 = replace(E069_17, E069_17 <= 0, NA),
         E110 = replace(E110, E110 <= 0, NA))

# Recode variable so they go from less to more: E069_11, E069_17, E110
wvs_clean$conf_gov <- recode(wvs_clean$E069_11,
                      "4" = 1,
                      "3" = 2,
                      "2" = 3,
                      "1" = 4) 

wvs_clean$conf_just <- recode(wvs_clean$E069_17,
                      "4" = 1,
                      "3" = 2,
                      "2" = 3,
                      "1" = 4) 

wvs_clean$sat_dem <- recode(wvs_clean$E110,
                      "4" = 1,
                      "3" = 2,
                      "2" = 3,
                      "1" = 4) 

```

E196 - Extent of political corruption
How widespread do you think bride taking and corruption is in this country?
1  Almost no public officials engaged in it
2  A few are
3  Most are
4  Almost all public officials are engaged in it

```{r}
table(wvs_clean$country, wvs_clean$E196)

wvs_extent_corruption <- wvs_clean %>%
  group_by(country, year,  ccode, E196) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_extent_corr = round(cnt / sum(cnt), 3))
```

E268 - Scale corruption in [my country] - pay a bribe, give a gift, do a favor to other to get things
1  There is no corruption in [my country]
2  2
3  3
4  4
5  5
6  6
7  7
8  8
9  9
10  There is abundant corruption in [my country]
```{r}
table(wvs_clean$country, wvs_clean$E268)
```
```{r}
#Recategorize into 4 categories
# 1-3 = 1
# 4-5 = 2
# 6-7 = 3
# 8-10 = 4}

wvs_clean$scale_corruption <- 0
wvs_clean$scale_corruption <- recode(wvs_clean$E268,
                                      "1" = 1,
                                      "2" = 1,
                                      "3" = 1,
                                      "4" = 2,
                                      "5" = 2,
                                      "6" = 3,
                                      "7" = 3,
                                      "8" = 4,
                                      "9" = 4,
                                      "10" = 4) 

wvs_scale_corruption <- wvs_clean %>%
  group_by(country, year, ccode, scale_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_scale_corr = round(cnt / sum(cnt), 3))
```

E269 - Groups of people involved in corruption: State authorities
1  None of them
2  Few of them
3  Most of them
4  All of them
```{r}
table(wvs_clean$country, wvs_clean$E269)
```
```{r}
wvs_groups_corruption <- wvs_clean %>%
  group_by(country, year, ccode, E269) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))
```

conf_gov - Confidence: The Government
1 None at all 
2 Not very much  
3 Quite a lot
4 A great deal
```{r}
table(wvs_clean$country, wvs_clean$conf_gov)
```
```{r}
wvs_conf_gov <- wvs_clean %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

wvs_conf_just <- wvs_clean %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

wvs_sat_dem <- wvs_clean %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))
```

Join WVS data
```{r}
wvs_conf_gov$year <- as.numeric(wvs_conf_gov$year)
wvs_conf_just$year <- as.numeric(wvs_conf_just$year)
wvs_extent_corruption$year <- as.numeric(wvs_extent_corruption$year)
wvs_groups_corruption$year <- as.numeric(wvs_groups_corruption$year)
wvs_sat_dem$year <- as.numeric(wvs_sat_dem$year)
wvs_scale_corruption$year <- as.numeric(wvs_scale_corruption$year)

wvs_conf_gov <- rename(wvs_conf_gov, scale = conf_gov)
wvs_conf_just <- rename(wvs_conf_just, scale = conf_just)
wvs_extent_corruption <- rename(wvs_extent_corruption, scale = E196)
wvs_groups_corruption <- rename(wvs_groups_corruption, scale = E269)
wvs_sat_dem <- rename(wvs_sat_dem, scale = sat_dem)
wvs_scale_corruption <- rename(wvs_scale_corruption, scale = scale_corruption)

wvs_final <- wvs_conf_gov %>%
  full_join(wvs_conf_just, by = c("country", "year", "ccode", "scale"))

wvs_final <- wvs_final %>%
  full_join(wvs_extent_corruption, by = c("country", "year", "ccode", "scale")) 

wvs_final <- wvs_final %>%
  full_join(wvs_groups_corruption, by = c("country", "year", "ccode", "scale")) 

wvs_final <- wvs_final %>%
  full_join(wvs_sat_dem, by = c("country", "year", "ccode", "scale")) 

wvs_final <- wvs_final %>%
  full_join(wvs_scale_corruption, by = c("country", "year", "ccode", "scale")) 

wvs_final <- select(wvs_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y,
                                  cnt.x.x.x, cnt.y.y.y))

openxlsx::write.xlsx(wvs_final, file = "wvs_final.xlsx",  keepNA = TRUE)
```

# Arab barometer

Wave 1

q253 - Here are some statements that describe how
widespread corruption and bribe taking are in
all sectors in [respondent’s country]. Which of
the following statements reflects your own
opinion the best?
1 = Hardly anyone is involved in corruption
 and bribery
2 = Not a lot of officials are corrupt
3 = Most officials are corrupt
4 = Almost everyone is corrupt
98 = Can’t Choose/Don’t know
99 = Decline to Answer

q254 - In your opinion, to what extent is the
government working to crackdown on
corruption and root out bribes?
1 = To a large extent
2 = To a medium extent
3 = To a small extent
4 = Not at all
97 = Not clear
98 = Can’t Choose/Don’t know
99 = Decline to Answer

I’m going to name a number of institutions. For each one, please tell me how much trust you have in them. Is it a great deal of trust, quite a lot of trust, not very much trust, or none at all?
q2011 - the prime minister
q2012 - the courts
1 = A great deal of trust
2 = Quite a lot of trust
3 = Not very much trust
4 = None at all
98 = Can’t Choose/Don’t know
99 = Decline to Answer

q244 - Using a similar 10-point scale, where 1 means
very unsatisfied and 10 means very satisfied,
indicate how satisfied you are with the
performance of the current [respondent’s
country] government
1 = Very unsatisfied
2 3 4 5 6 7 8 9
10 = Very satisfied
96 = Not important
97 = Not clear
98 = Can’t choose/Don’t know

```{r}
arab_wave1 <- read_csv("Data bases/Arab Barometer/wave1.csv")

arab_wave1$conf_gov <- recode(arab_wave1$q2011,
                             "none at all" = 1,
                             "not very much trust" = 2,
                             "quite a lot of trust" = 3,
                             "a great deal of trust" = 4)

#Create years
arab_wave1$year <- 0

arab_wave1$year[arab_wave1$country == "algeria"] <- "2006"
arab_wave1$year[arab_wave1$country == "bahrain"] <- "2009"
arab_wave1$year[arab_wave1$country == "jordan"] <- "2006"
arab_wave1$year[arab_wave1$country == "lebanon"] <- "2006"
arab_wave1$year[arab_wave1$country == "morocco"] <- "2007"
arab_wave1$year[arab_wave1$country == "palestine"] <- "2006"
arab_wave1$year[arab_wave1$country == "yemen"] <- "2007"

arab_wave1$country[arab_wave1$country == "algeria"] <- "Algeria"
arab_wave1$country[arab_wave1$country == "bahrain"] <- "Bahrain" 
arab_wave1$country[arab_wave1$country == "jordan"] <- "Jordan"
arab_wave1$country[arab_wave1$country == "lebanon"] <- "Lebanon" 
arab_wave1$country[arab_wave1$country == "morocco"] <- "Morocco" 
arab_wave1$country[arab_wave1$country == "palestine"] <- "Palestine"
arab_wave1$country[arab_wave1$country == "yemen"] <- "Yemen"

# Add country code
arab_wave1$ccode <- NA
arab_wave1$ccode <- countrycode(arab_wave1$country, origin = "country.name",
                             destination = "cown", warn = TRUE)

arab_wave1$conf_just <- recode(arab_wave1$q2012,
                             "none at all" = 1,
                             "not very much trust" = 2,
                             "quite a lot of trust" = 3,
                             "a great deal of trust" = 4)

arab_wave1$fight_corruption <- recode(arab_wave1$q254,
                             "not at all" = 1,
                             "to a small extent" = 2,
                             "to a medium extent" = 3,
                             "to a large extent" = 4)

arab_wave1$groups_corruption <- recode(arab_wave1$q253,
                             "hardly anyone is involved in corruption and bribery" = 1,
                             "not a lot of officials are corrupt" = 2,
                             "most officials are corrupt" = 3,
                             "almost everyone is corrupt" = 4)

# As WVS
#1  Not at all satisfied
#2  Not very satisfied
#3  Rather satisfied
#4  Very satisfied
arab_wave1$sat_dem <- recode(arab_wave1$q244,
                             "completely unsatisfied" = 1,
                             "2" = 1,
                             "3" = 1,
                             "4" = 2,
                             "5" = 2,
                             "6" = 3,
                             "7" = 3,
                             "8" = 4,
                             "9" = 4,
                             "completely satisfied" = 4)

arab_w1_conf_gov <- arab_wave1 %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

arab_w1_conf_just <- arab_wave1 %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

arab_w1_fight_corruption<- arab_wave1 %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

arab_w1_groups_corruption <- arab_wave1 %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

arab_w1_sat_dem <- arab_wave1 %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

arab_w1_conf_gov <- rename(arab_w1_conf_gov, scale = conf_gov)
arab_w1_conf_just <- rename(arab_w1_conf_just, scale = conf_just)
arab_w1_fight_corruption <- rename(arab_w1_fight_corruption, scale = fight_corruption)
arab_w1_groups_corruption <- rename(arab_w1_groups_corruption, scale = groups_corruption)
arab_w1_sat_dem <- rename(arab_w1_sat_dem, scale = sat_dem)

arab_w1_final <- arab_w1_conf_gov %>%
  full_join(arab_w1_conf_just, by = c("country", "year", "ccode", "scale"))

arab_w1_final <- arab_w1_final %>%
  full_join(arab_w1_fight_corruption, by = c("country", "year", "ccode", "scale")) 

arab_w1_final <- arab_w1_final %>%
  full_join(arab_w1_groups_corruption, by = c("country", "year", "ccode", "scale")) 

arab_w1_final <- arab_w1_final %>%
  full_join(arab_w1_sat_dem, by = c("country", "year", "ccode", "scale")) 


arab_w1_final <- select(arab_w1_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y,))
```

Wave 2
```{r}
arab_wave2 <- read_csv("Data bases/Arab Barometer/wave2.csv")

names(arab_wave2)
table(arab_wave2$country)
```

Create years
```{r}
arab_wave2$year <- 0

arab_wave2$year[arab_wave2$country == "1. Algeria"] <- "2011"
arab_wave2$year[arab_wave2$country == "5. Egypt"] <- "2011"
arab_wave2$year[arab_wave2$country == "7. Iraq"] <- "2011"
arab_wave2$year[arab_wave2$country == "8. Jordan"] <- "2010"
arab_wave2$year[arab_wave2$country == "10. Lebanon"] <- "2010"
arab_wave2$year[arab_wave2$country == "15. Palestine"] <- "2010"
arab_wave2$year[arab_wave2$country == "17. Saudi Arabia"] <- "2011"
arab_wave2$year[arab_wave2$country == "19. Sudan"] <- "2010"
arab_wave2$year[arab_wave2$country == "21. Tunisia"] <- "2011"
arab_wave2$year[arab_wave2$country == "22. Yemen"] <- "2011"

arab_wave2$country[arab_wave2$country == "1. Algeria"] <- "Algeria"
arab_wave2$country[arab_wave2$country == "5. Egypt"] <- "Egypt"
arab_wave2$country[arab_wave2$country == "7. Iraq"] <- "Iraq"
arab_wave2$country[arab_wave2$country == "8. Jordan"] <- "Jordan"
arab_wave2$country[arab_wave2$country == "10. Lebanon"] <- "Lebanon"
arab_wave2$country[arab_wave2$country == "15. Palestine"] <- "Palestine"
arab_wave2$country[arab_wave2$country == "17. Saudi Arabia"] <- "Saudi Arabia"
arab_wave2$country[arab_wave2$country == "19. Sudan"] <- "Sudan"
arab_wave2$country[arab_wave2$country == "21. Tunisia"] <- "Tunisia"
arab_wave2$country[arab_wave2$country == "22. Yemen"] <- "Yemen"

# Add country code
arab_wave2$ccode <- NA
arab_wave2$ccode <- countrycode(arab_wave2$country, origin = "country.name",
                             destination = "cown", warn = TRUE)
```


q513 - Suppose that there was a scale from 1-10 to measure the extent of your satisfaction with the government, in which 1 means that you were absolutely unsatisfied with its performance and 10
means that you were very satisfied, to what extent are you satisfied with the government’s
performance? 
```{r}
table(arab_wave2$q513)

arab_wave2$sat_dem <- recode(arab_wave2$q513,
                             "1. absolutely unsatisfied" = 1,
                             "2" = 1,
                             "3" = 1,
                             "4" = 2,
                             "5" = 2,
                             "6" = 3,
                             "7" = 3,
                             "8" = 4,
                             "9" = 4,
                             "10. very satisfied" = 4)
table(arab_wave2$sat_dem)
```

Fight corruption
```{r}
table(arab_wave2$q211)
arab_wave2$fight_corruption <- recode(arab_wave2$q211,
                             "4. not at all" = 1,
                             "3. to a limited extent" = 2,
                             "2. to a medium extent" = 3,
                             "1. to a great extent" = 4)

arab_w2_fight_corruption <- arab_wave2 %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))
```


Q201
q2011 The government (the
cabinet)
q2012  the judiciary
```{r}
arab_wave2$conf_gov <- recode(arab_wave2$q2011,
                             "4. i absolutely do not trust it" = 1,
                             "3. i trust it to a limited extent" = 2,
                             "2. i trust it to a medium extent" = 3,
                             "1. i trust it to a great extent" = 4)

arab_wave2$conf_just <- recode(arab_wave2$q2011,
                             "4. i absolutely do not trust it" = 1,
                             "3. i trust it to a limited extent" = 2,
                             "2. i trust it to a medium extent" = 3,
                             "1. i trust it to a great extent" = 4)

arab_w2_conf_gov <- arab_wave2 %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

arab_w2_conf_just <- arab_wave2 %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

arab_w2_sat_dem <- arab_wave2 %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

arab_w2_conf_gov <- rename(arab_w2_conf_gov, scale = conf_gov)
arab_w2_conf_just <- rename(arab_w2_conf_just, scale = conf_just)
arab_w2_fight_corruption <- rename(arab_w2_fight_corruption, scale = fight_corruption)
arab_w2_sat_dem <- rename(arab_w2_sat_dem, scale = sat_dem)

arab_w2_final <- arab_w2_conf_gov %>%
  full_join(arab_w2_conf_just, by = c("country", "year", "ccode", "scale"))

arab_w2_final <- arab_w2_final %>%
  full_join(arab_w2_fight_corruption, by = c("country", "year", "ccode", "scale")) 

arab_w2_final <- arab_w2_final %>%
  full_join(arab_w2_sat_dem, by = c("country", "year", "ccode", "scale")) 

names(arab_w2_final)

arab_w2_final <- select(arab_w2_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))
```

Wave 3

```{r}
arab_wave3 <- read_csv("Data bases/Arab Barometer/wave3.csv")

head(arab_wave3)
```

```{r}
arab_wave3$year <- 0

arab_wave3$year[arab_wave3$country == "Algeria"] <- "2013"
arab_wave3$year[arab_wave3$country == "Egypt"] <- "2013"
arab_wave3$year[arab_wave3$country == "Iraq"] <- "2013"
arab_wave3$year[arab_wave3$country == "Jordan"] <- "2012"
arab_wave3$year[arab_wave3$country == "Kuwait"] <- "2014"
arab_wave3$year[arab_wave3$country == "Lebanon"] <- "2013"
arab_wave3$year[arab_wave3$country == "Libya"] <- "2014"
arab_wave3$year[arab_wave3$country == "Morocco"] <- "2013"
arab_wave3$year[arab_wave3$country == "Palestine"] <- "2012"
arab_wave3$year[arab_wave3$country == "Sudan"] <- "2013"
arab_wave3$year[arab_wave3$country == "Tunisia"] <- "2013"
arab_wave3$year[arab_wave3$country == "Yemen"] <- "2013"

# Add country code
arab_wave3$ccode <- NA
arab_wave3$ccode <- countrycode(arab_wave3$country, origin = "country.name",
                             destination = "cown", warn = TRUE)
```

q201 - I will name a number of institutions, and I would like you to tell me to what extent you trust each of them:
q2011 - The government
No judiciary
```{r}
table(arab_wave3$q2011)

arab_wave3$conf_gov <- recode(arab_wave3$q2011,
                             "I absolutely do not trust it" = 1,
                             "I trust it to a limited extent" = 2,
                             "I trust it to a medium extent" = 3,
                             "I trust it to a great extent" = 4)

table(arab_wave3$conf_gov)
```


Fight corruption q211
```{r}
table(arab_wave3$q211)

arab_wave3$fight_corruption <- recode(arab_wave3$q211,
                             "Not at all" = 1,
                             "To a limited extent" = 2,
                             "To a medium extent" = 3,
                             "To a great extent" = 4)
```

Satisfaction democracy
```{r}
table(arab_wave3$q513)

arab_wave3$sat_dem <- recode(arab_wave3$q513,
                             "Absolutely unsatisfied" = 1,
                             "2" = 1,
                             "3" = 1,
                             "4" = 2,
                             "5" = 2,
                             "6" = 3,
                             "7" = 3,
                             "8" = 4,
                             "9" = 4,
                             "Completely satisfied" = 4)
table(arab_wave3$sat_dem)
```

```{r}
arab_w3_fight_corruption <- arab_wave3 %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

arab_w3_conf_gov <- arab_wave3 %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

arab_w3_sat_dem <- arab_wave3 %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

arab_w3_fight_corruption <- rename(arab_w3_fight_corruption, scale = fight_corruption)
arab_w3_conf_gov <- rename(arab_w3_conf_gov, scale = conf_gov)
arab_w3_sat_dem <- rename(arab_w3_sat_dem, scale = sat_dem)

arab_w3_final <- arab_w3_fight_corruption %>%
  full_join(arab_w3_conf_gov, by = c("country", "year", "ccode", "scale"))

arab_w3_final <- arab_w3_final %>%
  full_join(arab_w3_sat_dem, by = c("country", "year", "ccode",  "scale")) 

arab_w3_final <- select(arab_w3_final, -c(cnt.x, cnt.y))

```

Wave 4
```{r}
arab_wave4 <- read_csv("Data bases/Arab Barometer/wave4.csv")
head(arab_wave4)

arab_wave4$year <- 0

arab_wave4$year[arab_wave4$country == "Algeria"] <- "2016"
arab_wave4$year[arab_wave4$country == "Egypt"] <- "2016"
arab_wave4$year[arab_wave4$country == "Jordan"] <- "2016"
arab_wave4$year[arab_wave4$country == "Lebanon"] <- "2016"
arab_wave4$year[arab_wave4$country == "Morocco"] <- "2016"
arab_wave4$year[arab_wave4$country == "Palestine"] <- "2016"
arab_wave4$year[arab_wave4$country == "Tunisia"] <- "2016"

# Add country code
arab_wave4$ccode <- NA
arab_wave4$ccode <- countrycode(arab_wave4$country, origin = "country.name",
                             destination = "cown", warn = TRUE)
```

Extent corruption - q210
```{r}
table(arab_wave4$q210)

arab_wave4$extent_corruption <- recode(arab_wave4$q210,
                             "Not at all" = 1,
                             "To a small extent" = 2,
                             "To a medium extent" = 3,
                             "To a large extent" = 4)
```


Fight corruption - q211
```{r}
table(arab_wave4$q211)

arab_wave4$fight_corruption <- recode(arab_wave4$q211,
                             "Not at all" = 1,
                             "To a small extent" = 2,
                             "To a medium extent" = 3,
                             "To a large extent" = 4)
```

Confidence Government - q2011
Confidence Justice - q2012
```{r}
table(arab_wave4$q2011)
arab_wave4$conf_gov <- recode(arab_wave4$q2011,
                             "No trust at all" = 1,
                             "Not very much trust" = 2,
                             "Quite a lot of trust" = 3,
                             "A great deal of trust" = 4)

arab_wave4$conf_just <- recode(arab_wave4$q2012,
                             "No trust at all" = 1,
                             "Not very much trust" = 2,
                             "Quite a lot of trust" = 3,
                             "A great deal of trust" = 4)
```

Satisfaction democracy
```{r}
table(arab_wave4$q513)

arab_wave4$sat_dem <- recode(arab_wave4$q513,
                             "Completely unsatisfied" = 1,
                             "2" = 1,
                             "3" = 1,
                             "4" = 2,
                             "5" = 2,
                             "6" = 3,
                             "7" = 3,
                             "8" = 4,
                             "9" = 4,
                             "Completely satisfied" = 4)
```

```{r}
arab_w4_extent_corruption <- arab_wave4 %>%
  group_by(country, year, ccode, extent_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_ext_corr = round(cnt / sum(cnt), 3))

arab_w4_fight_corruption <- arab_wave4 %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

arab_w4_conf_gov <- arab_wave4 %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

arab_w4_conf_just <- arab_wave4 %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

arab_w4_sat_dem <- arab_wave4 %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

arab_w4_extent_corruption <- rename(arab_w4_extent_corruption, scale = extent_corruption)
arab_w4_fight_corruption <- rename(arab_w4_fight_corruption, scale = fight_corruption)
arab_w4_conf_gov <- rename(arab_w4_conf_gov, scale = conf_gov)
arab_w4_conf_just <- rename(arab_w4_conf_just, scale = conf_just)
arab_w4_sat_dem <- rename(arab_w4_sat_dem, scale = sat_dem)

arab_w4_final <- arab_w4_extent_corruption %>%
  full_join(arab_w4_fight_corruption, by = c("country", "year", "ccode", "scale"))

arab_w4_final <- arab_w4_final %>%
  full_join(arab_w4_conf_gov, by = c("country", "year", "ccode", "scale")) 

arab_w4_final <- arab_w4_final %>%
  full_join(arab_w4_conf_just, by = c("country", "year", "ccode", "scale")) 

arab_w4_final <- arab_w4_final %>%
  full_join(arab_w4_sat_dem, by = c("country", "year", "ccode", "scale")) 

arab_w4_final <- select(arab_w4_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))
```

Wave 5

```{r}
arab_wave5 <- read_csv("Data bases/Arab Barometer/wave5.csv")

arab_wave5$country <- recode(arab_wave5$country,
                             "1" = "Algeria",
                             "5" = "Egypt",
                             "7" = "Iraq",
                             "8" = "Jordan",
                             "9" = "Kuwait",
                             "10" = "Lebanon",
                             "11" = "Libya",
                             "13" = "Morocco",
                             "15" = "Palestine",
                             "19" = "Sudan",
                             "21" = "Tunisia",
                             "22" = "Yemen")

# Add country code
arab_wave5$ccode <- NA
arab_wave5$ccode <- countrycode(arab_wave5$country, origin = "country.name",
                             destination = "cown", warn = TRUE)

arab_wave5$year <- 0

arab_wave5$year[arab_wave5$country == "Algeria"] <- "2019"
arab_wave5$year[arab_wave5$country == "Egypt"] <- "2018"
arab_wave5$year[arab_wave5$country == "Iraq"] <- "2019"
arab_wave5$year[arab_wave5$country == "Jordan"] <- "2018"
arab_wave5$year[arab_wave5$country == "Kuwait"] <- "2019"
arab_wave5$year[arab_wave5$country == "Lebanon"] <- "2018"
arab_wave5$year[arab_wave5$country == "Libya"] <- "2019"
arab_wave5$year[arab_wave5$country == "Morocco"] <- "2018"
arab_wave5$year[arab_wave5$country == "Palestine"] <- "2018"
arab_wave5$year[arab_wave5$country == "Sudan"] <- "2018"
arab_wave5$year[arab_wave5$country == "Tunisia"] <- "2018"
arab_wave5$year[arab_wave5$country == "Yemen"] <- "2018"
```

Confidence - Q201a. [PROGRAMMER: SEE SPECIFIC ITEMS] I’m going to name a number of institutions.
For each one, please tell me how much trust you have in them
Q201A_1 - Government
Q201A_2 - Courts

```{r}
table(arab_wave5$Q201A_1)
table(arab_wave5$Q201A_2)
# 1 = a great deal of trust
# 4 = no trust at all

arab_wave5$conf_gov <- recode(arab_wave5$Q201A_1,
                             "4" = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

arab_wave5$conf_just <- recode(arab_wave5$Q201A_2,
                             "4" = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

arab_wave5 <- 
  arab_wave5 %>% 
  mutate(conf_gov = replace(conf_gov, conf_gov >= 5, NA),
         conf_just = replace(conf_just, conf_just >= 5, NA))
    
table(arab_wave5$conf_gov)
table(arab_wave5$conf_just)
```


Extent corruption
Q210. [PROGRAMMER: IF COUNTRY != 1] To what extent do you think that there is
corruption within the national state agencies and institutions in your country?
1. To a large extent
2. To a medium extent
3. To a small extent
4. Not at all 

```{r}
table(arab_wave5$Q210)

arab_wave5$extent_corruption <- recode(arab_wave5$Q210,
                             "4 " = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

table(arab_wave5$extent_corruption)
arab_wave5 <- 
  arab_wave5 %>% 
  mutate(extent_corruption = replace(extent_corruption, extent_corruption >= 5, NA))
```

Q211. [PROGRAMMER: IF COUNTRY != 1 & Q210 == 1, 2 OR 3] In your opinion, to what
extent is the national government working to crackdown on corruption?
1. To a large extent
2. To a medium extent
3. To a small extent
4. Not at all
```{r}
table(arab_wave5$Q211)

arab_wave5$fight_corruption <- recode(arab_wave5$Q211,
                             "4 " = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

table(arab_wave5$fight_corruption)

arab_wave5 <- 
  arab_wave5 %>% 
  mutate(fight_corruption = replace(fight_corruption, fight_corruption >= 5, NA))
```

Q211a. [PROGRAMMER: IF COUNTRY != 1 & Q210 == 1,2 OR 3] How widespread do you
think corruption is in your local / municipal government. Would you say …? [IF COUNTRY ==
21 (state government)]
1. Hardly anyone is involved
2. Not a lot of officials are corrupt
3. Most officials are corrupt
4. Almost everyone is corrupt
```{r}
table(arab_wave5$Q211A)

arab_wave5$groups_corruption <- arab_wave5$Q211A

table(arab_wave5$groups_corruption)

arab_wave5 <- 
  arab_wave5 %>% 
  mutate(groups_corruption = replace(groups_corruption, groups_corruption >= 5, NA))
```

Q513. [PROGRAMMER: IF COUNTRY != 1 OR 9] On a scale from 0-10 measuring the
extent of your satisfaction with the current government’s performance, in which 0 means that you
are completely dissatisfied with its performance and 10 means you are completely satisfied. To
what extent are you satisfied with the current government’s performance? 
```{r}
table(arab_wave5$Q513)

arab_wave5$sat_dem <- recode(arab_wave5$Q513,
                             "0" = 1,
                             "2" = 1,
                             "3" = 1,
                             "4" = 2,
                             "5" = 2,
                             "6" = 3,
                             "7" = 3,
                             "8" = 4,
                             "9" = 4,
                             "10" = 4)

table(arab_wave5$sat_dem)

arab_wave5 <- 
  arab_wave5 %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA))
```

```{r}
arab_w5_conf_gov <- arab_wave5 %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

arab_w5_conf_just <- arab_wave5 %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

arab_w5_extent_corruption <- arab_wave5 %>%
  group_by(country, year, ccode, extent_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_ext_corr = round(cnt / sum(cnt), 3))

arab_w5_fight_corruption <- arab_wave5 %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

arab_w5_sat_dem <- arab_wave5 %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

arab_w5_conf_gov <- rename(arab_w5_conf_gov, scale = conf_gov)
arab_w5_conf_just <- rename(arab_w5_conf_just, scale = conf_just)
arab_w5_extent_corruption <- rename(arab_w5_extent_corruption, scale = extent_corruption)
arab_w5_fight_corruption  <- rename(arab_w5_fight_corruption, scale = fight_corruption)
arab_w5_sat_dem <- rename(arab_w5_sat_dem, scale = sat_dem)

arab_w5_final <- arab_w5_conf_gov %>%
  full_join(arab_w5_conf_just, by = c("country", "year", "ccode", "scale")) 

arab_w5_final <- arab_w5_final %>%
  full_join(arab_w5_extent_corruption, by = c("country", "year", "ccode", "scale")) 

arab_w5_final <- arab_w5_final %>%
  full_join(arab_w5_fight_corruption, by = c("country", "year", "ccode", "scale"))

arab_w5_final <- arab_w5_final %>%
  full_join(arab_w5_sat_dem, by = c("country", "year", "ccode", "scale")) 

arab_w5_final <- select(arab_w5_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))
```

Wave 6

```{r}
arab_w6_part1 <- read_csv("Data bases/Arab Barometer/wave6_part1.csv")
arab_w6_part2 <- read_csv("Data bases/Arab Barometer/wave6_part2.csv")
arab_w6_part3 <- read_csv("Data bases/Arab Barometer/wave6_part3.csv")

# Select specific columns
arab_w6_part1 <- select(arab_w6_part1, c(COUNTRY, DATE, Q201A_1, Q201A_2, Q210, Q211, Q204A_3))
arab_w6_part2 <- select(arab_w6_part2, c(COUNTRY, DATE, Q201A_1, Q201A_2, Q210))
arab_w6_part3 <- select(arab_w6_part3, c(COUNTRY, DATE, Q201A_1, Q201A_2, Q210, Q211, Q204A_3))

arab_w6_part2$Q211 <- NA
arab_w6_part2$Q204A_3 <- NA

arab_wave6 <- rbind(arab_w6_part1, arab_w6_part2)
arab_wave6 <- rbind(arab_wave6, arab_w6_part3)
names(arab_wave6)
```

```{r}
arab_wave6$country <- recode(arab_wave6$COUNTRY,
                             "1" = "Algeria",
                             "7" = "Iraq",
                             "8" = "Jordan",
                             "10" = "Lebanon",
                             "11" = "Libya",
                             "13" = "Morocco",
                             "21" = "Tunisia")

# Add country code
arab_wave6$ccode <- NA
arab_wave6$ccode <- countrycode(arab_wave6$country, origin = "country.name",
                             destination = "cown", warn = TRUE)

table(arab_wave6$country)

arab_wave6$year <- format(as.Date(arab_wave6$DATE, format="%Y-%m-%d"),"%Y")
```

Trust in the government - Q201A_1
Trust in Courts - Q201A_2
1. A great deal of trust
2. Quite a lot of trust
3. Not a lot of trust
4. No trust at all

```{r}
table(arab_wave6$Q201A_1)
table(arab_wave6$Q201A_2)
# 1 = a great deal of trust
# 4 = no trust at all

arab_wave6$conf_gov <- recode(arab_wave6$Q201A_1,
                             "4" = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

arab_wave6$conf_just <- recode(arab_wave6$Q201A_2,
                             "4" = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

arab_wave6 <- 
  arab_wave6 %>% 
  mutate(conf_gov = replace(conf_gov, conf_gov >= 5, NA),
         conf_just = replace(conf_just, conf_just >= 5, NA))
    
table(arab_wave6$conf_gov)
table(arab_wave6$conf_just)
```

Q210 To what extent do you think that there is corruption within the national
state agencies and institutions in your country?
1. To a large extent
2. To a medium extent
3. To a small extent
4. Not at all
```{r}
table(arab_wave6$Q210)

arab_wave6$extent_corruption <- recode(arab_wave6$Q210,
                             "4 " = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

table(arab_wave6$extent_corruption)

arab_wave6 <- 
  arab_wave6 %>% 
  mutate(extent_corruption = replace(extent_corruption, extent_corruption >= 5, NA))
```

Q211 [PROGRAMMER: IF Q210 == 1, 2 OR 3] In your opinion, to what extent is
the national government working to crackdown on corruption? [NOTE TO
INTERVIEWER ON PHONE SURVEYS IN LIBYA: If asked, please tell the
respondent that the question is asking about the government who controls
the area where the respondent lives.]
1. To a large extent
2. To a medium extent
3. To a small extent
4. Not at all 
```{r}
table(arab_wave6$Q211)

arab_wave6$fight_corruption <- recode(arab_wave6$Q211,
                             "4 " = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

table(arab_wave6$fight_corruption)

arab_wave6 <- 
  arab_wave6 %>% 
  mutate(fight_corruption = replace(fight_corruption, fight_corruption >= 5, NA))
```

Q204A How satisfied are you with the following?
1. Completely satisfied
2. Satisfied
3. Dissatisfied
4. Completely dissatisfied

The government’s performance
overall [

```{r}
table(arab_wave6$Q204A_3)

arab_wave6$sat_dem <- recode(arab_wave6$Q204A_3,
                             "4" = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

table(arab_wave6$sat_dem)

arab_wave6 <- 
  arab_wave6 %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA))
```

Join
```{r}
arab_w6_conf_gov <- arab_wave6 %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

arab_w6_conf_just <- arab_wave6 %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

arab_w6_extent_corruption <- arab_wave6 %>%
  group_by(country, year, ccode, extent_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_ext_corr = round(cnt / sum(cnt), 3))

arab_w6_sat_dem <- arab_wave6 %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

arab_w6_conf_gov <- rename(arab_w6_conf_gov, scale = conf_gov)
arab_w6_conf_just <- rename(arab_w6_conf_just, scale = conf_just)
arab_w6_extent_corruption <- rename(arab_w6_extent_corruption, scale = extent_corruption)
arab_w6_sat_dem <- rename(arab_w6_sat_dem, scale = sat_dem)

arab_w6_final <- arab_w6_conf_gov %>%
  full_join(arab_w6_conf_just, by = c("country", "year", "ccode", "scale")) 

arab_w6_final <- arab_w6_final %>%
  full_join(arab_w6_extent_corruption, by = c("country", "year", "ccode", "scale")) 

arab_w6_final <- arab_w6_final %>%
  full_join(arab_w6_sat_dem, by = c("country", "year", "ccode", "scale")) 

arab_w6_final <- select(arab_w6_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))
```

Join all Arabbarometer
```{r}
arab_final <- arab_w1_final %>%
  full_join(arab_w2_final)

arab_final <- arab_final %>%
  full_join(arab_w3_final)

arab_final <- arab_final %>%
  full_join(arab_w4_final)

arab_final <- arab_final %>%
  full_join(arab_w5_final)

arab_final <- arab_final %>%
  full_join(arab_w6_final)

table(arab_final$country)
```


# Africanbarometer

Wave 1
Codebook: https://www.afrobarometer.org/wp-content/uploads/2022/02/merged_r1_codebook2.pdf
```{r}
merged_r1_data <- read_sav("Data bases/Africanbarometer/merged_r1_data.sav")
names(merged_r1_data)
```

```{r}
table(merged_r1_data$country)
```

```{r}
merged_r1_data$country <- as.numeric(merged_r1_data$country)
merged_r1_data <- merged_r1_data %>%
  mutate(country = recode(country,
                          "1" = "Botswana",
                          "2" = "Ghana",
                          "3" = "Lesotho",
                          "4" = "Malawi",
                          "5" = "Mali",
                          "6" = "Namibia",
                          "7" = "Nigeria",
                          "8" = "South Africa",
                          "9" = "Tanzania",
                          "10" = "Uganda",
                          "11" = "Zambia",
                          "12" = "Zimbabwe"))
table(merged_r1_data$country)

# Create country code
merged_r1_data$ccode <- NA
merged_r1_data$ccode <- countrycode(merged_r1_data$country, origin = "country.name",
                             destination = "cown", warn = TRUE)
```

```{r}
merged_r1_data$year <- 0

merged_r1_data$year[merged_r1_data$country == "Botswana"] <- "1999"
merged_r1_data$year[merged_r1_data$country == "Ghana"] <- "1999"
merged_r1_data$year[merged_r1_data$country == "Lesotho"] <- "2000"
merged_r1_data$year[merged_r1_data$country == "Malawi"] <- "1999"
merged_r1_data$year[merged_r1_data$country == "Mali"] <- "2001"
merged_r1_data$year[merged_r1_data$country == "Namibia"] <- "1999"
merged_r1_data$year[merged_r1_data$country == "Nigeria"] <- "1999"
merged_r1_data$year[merged_r1_data$country == "South Africa"] <- "2000"
merged_r1_data$year[merged_r1_data$country == "Tanzania"] <- "2001"
merged_r1_data$year[merged_r1_data$country ==  "Uganda"] <- "2000"
merged_r1_data$year[merged_r1_data$country ==  "Zambia"] <- "1999"
merged_r1_data$year[merged_r1_data$country ==  "Zimbabwe"] <- "1999"
```

Variable name: trspre
Variable label: Trust the president
Values: 1-4, 9, 98, 99
Value Labels: 1=I do not trust them at all/Never, 2=I distrust them somewhat/Sometimes, 3=I trust them
somewhat/Most times, 4=I trust them a lot/Always, 9=Don’t Know, 98=Refused to Answer, 99=Missing
Data
```{r}
table(merged_r1_data$trspre)

merged_r1_data <- 
  merged_r1_data %>% 
  mutate(conf_gov = replace(trspre, trspre >= 5, NA))
```


Variable name: trscts
Variable label: Trust courts of law
Values: 1-4, 9, 98, 99
Value Labels: 1=I do not trust them at all/Never, 2=I distrust them somewhat/Sometimes, 3=I trust them
somewhat/Most times, 4=I trust them a lot/Always, 9=Don’t Know, 98=Refused to Answer, 99=Missing
Data 
```{r}
table(merged_r1_data$trscts)

merged_r1_data <- 
  merged_r1_data %>% 
  mutate(conf_just = replace(trscts, trscts >= 5, NA))
```


Variable name: pfpcr2
Variable label: Extent of corruption/bribery
Corruption is a fact of life 
Values: 1-5, 9, 98, 99
Value Labels: 1=Strongly disagree/Almost all, 2=Disagree/Most, 3=Agree/A few/Some, 4=Strongly
agree/Almost none, 9=Don’t Know, 98=Refused to Answer, 99=Missing Data 
```{r}
table(merged_r1_data$pfpcr2)

merged_r1_data$pfpcr2 <- as.numeric(merged_r1_data$pfpcr2)
merged_r1_data$extent_corruption <- recode(merged_r1_data$pfpcr2,
                             "4" = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

merged_r1_data <- 
  merged_r1_data %>% 
  mutate(extent_corruption = replace(pfpcr2, pfpcr2 >= 5, NA))

table(merged_r1_data$extent_corruption)
```


Variable name: pfpcr1
Variable label: Handling corruption
Values: 1-4, 9, 98, 99
Value Labels: 1=Very badly/Not al all well, 2=Quite badly/Not very well, 3=Fairly well, 4=Very well,
9=Don’t Know, 98=Refused to Answer, 99=Missing Data
Notes: Not asked in Namibia and Zimbabwe
```{r}
table(merged_r1_data$pfpcr1)

merged_r1_data <- 
  merged_r1_data %>% 
  mutate(fight_corruption = replace(pfpcr1, pfpcr1 >= 5, NA))
table(merged_r1_data$fight_corruption)
```


Groups corruption:
Variable name: pfpcr3
Variable label: Corruption among elected leaders
Values: 1-4, 9, 98, 99
Value Labels: 1=Very common/Almost all, 2=Fairly common/Most, 3=Fairly rare/A few/Some, 4=Very
rare/Almost none, 9=Don’t Know, 98=Refused to Answer, 99=Missing Data
Notes: Not asked in Ghana and Nigeria
```{r}
table(merged_r1_data$pfpcr3)

merged_r1_data$pfpcr3 <- as.numeric(merged_r1_data$pfpcr3)
merged_r1_data$groups_corruption <- recode(merged_r1_data$pfpcr3,
                             "4" = 1,
                             "3" = 2,
                             "2" = 3,
                             "1" = 4)

merged_r1_data <- 
  merged_r1_data %>% 
  mutate(groups_corruption = replace(pfpcr3, pfpcr3 >= 5, NA))
table(merged_r1_data$groups_corruption)
```


Variable name: dmpsat
Variable label: Satisfaction with democracy
Values: 0-5, 9, 97, 98, 99
Value Labels: 0=This country is not a democracy, 1=Very dissatisfied, 2=Somewhat dissatisfied,
3=Neutral, 4=Somewhat satisfied, 5=Very satisfied, 9=Don’t Know, 97=Not Applicable, 98=Refused to
Answer, 99=Missing Data 
```{r}
table(merged_r1_data$dmpsat)

merged_r1_data$dmpsat <- as.numeric(merged_r1_data$dmpsat)
merged_r1_data$sat_dem <- recode(merged_r1_data$dmpsat,
                             "1" = 1,
                             "2" = 2,
                             "3" = 3,
                             "4" = 3,
                             "5" = 4)

merged_r1_data <- 
  merged_r1_data %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA),
         sat_dem = replace(sat_dem, sat_dem == 0, NA))

table(merged_r1_data$sat_dem)
```

Join
```{r}
afr_w1_conf_gov <- merged_r1_data %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

afr_w1_conf_just <- merged_r1_data %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

afr_w1_extent_corruption <- merged_r1_data %>%
  group_by(country, year, ccode, extent_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_ext_corr = round(cnt / sum(cnt), 3))

afr_w1_fight_corruption <- merged_r1_data %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

afr_w1_groups_corruption <- merged_r1_data %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

afr_w1_sat_dem <- merged_r1_data %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

afr_w1_conf_gov <- rename(afr_w1_conf_gov, scale = conf_gov)
afr_w1_conf_just <- rename(afr_w1_conf_just, scale = conf_just)
afr_w1_extent_corruption <- rename(afr_w1_extent_corruption, scale = extent_corruption)
afr_w1_fight_corruption <- rename(afr_w1_fight_corruption, scale = fight_corruption)
afr_w1_groups_corruption <- rename(afr_w1_groups_corruption, scale = groups_corruption)
afr_w1_sat_dem <- rename(afr_w1_sat_dem, scale = sat_dem)

africa_w1_final <- afr_w1_conf_gov %>%
  full_join(afr_w1_conf_just, by = c("country", "year", "ccode", "scale")) 

africa_w1_final <- africa_w1_final %>%
  full_join(afr_w1_extent_corruption, by = c("country", "year", "ccode", "scale")) 

africa_w1_final <- africa_w1_final %>%
  full_join(afr_w1_fight_corruption, by = c("country", "year", "ccode", "scale")) 

africa_w1_final <- africa_w1_final %>%
  full_join(afr_w1_groups_corruption, by = c("country", "year", "ccode", "scale")) 

africa_w1_final <- africa_w1_final %>%
  full_join(afr_w1_sat_dem, by = c("country", "year", "ccode", "scale")) 

names(africa_w1_final)
africa_w1_final <- select(africa_w1_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y, cnt.x.x.x, cnt.y.y.y))
```

Wave 2
```{r}
merged_r2_data <- read_sav("Data bases/Africanbarometer/merged_r2_data.sav")
names(merged_r2_data)
```


```{r}
table(merged_r2_data$country)
```

```{r}
merged_r2_data$country <- as.numeric(merged_r2_data$country)
merged_r2_data <- merged_r2_data %>%
  mutate(country = recode(country,
                          "1" = "Botswana",
                          "2" = "Ghana",
                          "3" = "Lesotho",
                          "4" = "Malawi",
                          "5" = "Mali",
                          "6" = "Namibia",
                          "7" = "Nigeria",
                          "8" = "South Africa",
                          "9" = "Tanzania",
                          "10" = "Uganda",
                          "11" = "Zambia",
                          "12" = "Zimbabwe",
                          "13" = "Cape Verde",
                          "14" = "Kenya",
                          "15" = "Mozambique",
                          "16" = "Senegal"))
table(merged_r2_data$country)

# Create country code
merged_r2_data$ccode <- NA
merged_r2_data$ccode <- countrycode(merged_r2_data$country, origin = "country.name",
                                    destination = "cown", warn = TRUE)
```

```{r}
table(merged_r2_data$dateintr)

merged_r2_data$year <- format(as.Date(merged_r2_data$dateintr, format="%Y-%m-%d"),"%Y")

table(merged_r2_data$year)
table(merged_r2_data$year, merged_r2_data$country)

merged_r2_data$year[merged_r2_data$country ==  "Senegal"] <- "2002"
```

Question Number: Q43A
Question: How much do you trust each of the following, or haven’t you heard enough about them to say: The
President?
Variable label: Trust the President
Values: 0-3, 9, 98, -1
Value Labels: 0=Not at all, 1=A little bit, 2=A lot, 3=A very great deal, 9=Don’t Know/Haven’t Heard Enough,
98=Refused to Answer, -1=Missing Data
```{r}
table(merged_r2_data$q43a)
merged_r2_data$q43a <- as.numeric(merged_r2_data$q43a)

merged_r2_data$q43a <- recode(merged_r2_data$q43a,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r2_data <- 
  merged_r2_data %>% 
  mutate(conf_gov = replace(q43a, q43a >= 5, NA))

table(merged_r2_data$conf_gov)
```


Question Number: Q43J
Question: How much do you trust each of the following, or haven’t you heard enough about them to say: Courts of
Law?
Variable label: Trust courts of law
Values: 0-3, 9, 98, -1
Value Labels: 0=Not at all, 1=A little bit, 2=A lot, 3=A very great deal, 9=Don’t Know/Haven’t Heard Enough,
98=Refused to Answer, -1=Missing Data
```{r}
table(merged_r2_data$q43j)
merged_r2_data$q43j <- as.numeric(merged_r2_data$q43j)

merged_r2_data$q43j <- recode(merged_r2_data$q43j,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r2_data <- 
  merged_r2_data %>% 
  mutate(conf_just = replace(q43j, q43j >= 5, NA))
table(merged_r2_data$conf_just)
```

Question Number: Q45J
Question: How well or badly would you say the current government is handling the following matters, or haven’t
you heard enough about them to say: Fighting corruption in government?
Variable label: Handling fighting corruption in government
Values: 1-4, 9, 98, -1
Value Labels: 1=Very Badly, 2=Fairly Badly, 3=Fairly Well, 4=Very Well, 9=Don’t Know/Haven’t heard enough,
98=Refused to Answer, -1=Missing Data
```{r}
table(merged_r2_data$q45j)
merged_r2_data$q45j <- as.numeric(merged_r2_data$q45j)

merged_r2_data <- 
  merged_r2_data %>% 
  mutate(fight_corruption = replace(q45j, q45j > 5 | q45j <=-1, NA))

table(merged_r2_data$fight_corruption)
```


Question Number: Q51C
Question: How many of the following people do you think are involved in corruption, or haven’t you heard enough
about them to say: Government officials?
Variable label: Corruption: Government officials
Values: 0-3, 9, 98, -1
Value Labels: 0=None, 1=Some of them, 2=Most of them, 3=All of them, 9=Don’t Know, 98=Refused to Answer,
-1=Missing Data
```{r}
table(merged_r2_data$q51c)

merged_r2_data$q51c <- as.numeric(merged_r2_data$q51c)
merged_r2_data$groups_corruption <- recode(merged_r2_data$q51c,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r2_data <- 
  merged_r2_data %>% 
  mutate(groups_corruption = replace(groups_corruption, groups_corruption >= 5, NA))

table(merged_r2_data$groups_corruption)
```


Question Number: Q40
Question: Overall, how satisfied are you with the way democracy works in [country name]? Are you:
Variable label: Satisfaction with democracy
Values: 0-4, 9, 98, -1
Value Labels: 0=[Country] is not a democracy, 1=Not at All Satisfied, 2=Not Very Satisfied, 3=Fairly Satisfied,
4=Very Satisfied, 9=Don’t Know, 98=Refused to Answer, -1=Missing Data
```{r}
table(merged_r2_data$q40)
merged_r2_data$q40 <- as.numeric(merged_r2_data$q40)

merged_r2_data$sat_dem <- recode(merged_r2_data$q40,
                             "-1" = 99,
                             "0" = 99)

merged_r2_data <- 
  merged_r2_data %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA))

table(merged_r2_data$sat_dem)
```

Join
```{r}
conf_gov_afr_w2 <- merged_r2_data %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

conf_just_afr_w2 <- merged_r2_data %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

fight_corruption_afr_w2 <- merged_r2_data %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

groups_corruption_afr_w2 <- merged_r2_data %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

sat_dem_afr_w2 <- merged_r2_data %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

conf_gov_afr_w2 <- rename(conf_gov_afr_w2, scale = conf_gov)
conf_just_afr_w2 <- rename(conf_just_afr_w2, scale = conf_just)
fight_corruption_afr_w2 <- rename(fight_corruption_afr_w2, scale = fight_corruption)
groups_corruption_afr_w2 <- rename(groups_corruption_afr_w2, scale = groups_corruption)
sat_dem_afr_w2 <- rename(sat_dem_afr_w2, scale = sat_dem)

africa_w2_final <- conf_gov_afr_w2 %>%
  full_join(conf_just_afr_w2, by = c("country", "year", "ccode", "scale")) 

africa_w2_final <- africa_w2_final %>%
  full_join(fight_corruption_afr_w2, by = c("country", "year", "ccode", "scale")) 

africa_w2_final <- africa_w2_final %>%
  full_join(groups_corruption_afr_w2, by = c("country", "year", "ccode", "scale")) 

africa_w2_final <- africa_w2_final %>%
  full_join(sat_dem_afr_w2, by = c("country", "year", "ccode", "scale")) 

names(africa_w2_final)
africa_w2_final <- select(africa_w2_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))

```

Wave 3
```{r}
merged_r3_data <- read_sav("Data bases/Africanbarometer/merged_r3_data.sav")
names(merged_r3_data)
```

```{r}
table(merged_r3_data$country)
```

```{r}
merged_r3_data$country <- as.numeric(merged_r3_data$country)

merged_r3_data <- merged_r3_data %>%
  mutate(country = recode(country,
                          "1" = "Benin",
                          "2" = "Botswana",
                          "3" = "Cape Verde",
                          "4" = "Ghana",
                          "5" = "Kenya",
                          "6" = "Lesotho",
                          "7" = "Madagascar",
                          "8" = "Malawi",
                          "9" = "Mali",
                          "10" = "Mozambique",
                          "11" = "Namibia",
                          "12" = "Nigeria",
                          "13" = "Senegal",
                          "14" = "South Africa",
                          "15" = "Tanzania",
                          "16" = "Uganda",
                          "17" = "Zambia",
                          "18" = "Zimbabwe"))

table(merged_r3_data$country)

# Create country code
merged_r3_data$ccode <- NA
merged_r3_data$ccode <- countrycode(merged_r3_data$country, origin = "country.name",
                                    destination = "cown", warn = TRUE)
```

```{r}
table(merged_r3_data$dateintr)

merged_r3_data$year <- format(as.Date(merged_r3_data$dateintr, format="%Y-%m-%d"),"%Y")

table(merged_r3_data$year)
table(merged_r3_data$year, merged_r3_data$country)
```
Question Number: Q55A
Question: How much do you trust each of the following, or haven’t you heard enough about them to say: The
President/Prime Minister?
Variable Label: Trust the President
Values: 0-3, 9, 98, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t Know/Haven’t Heard Enough,
98=Refused to Answer, -1=Missing Data 
```{r}
table(merged_r3_data$q55a)
merged_r3_data$q55a <- as.numeric(merged_r3_data$q55a)

merged_r3_data$q55a <- recode(merged_r3_data$q55a,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r3_data <- 
  merged_r3_data %>% 
  mutate(conf_gov = replace(q55a, q55a >= 5, NA))

table(merged_r3_data$conf_gov)
```


Question Number: Q55I
Question: How much do you trust each of the following, or haven’t you heard enough about them to say: Courts of
Law?
Variable Label: Trust courts of law
Values: 0-3, 9, 98, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t Know/Haven’t Heard Enough,
98=Refused to Answer, -1=Missing Data 
```{r}
table(merged_r3_data$q55i)
merged_r3_data$q55i <- as.numeric(merged_r3_data$q55i)

merged_r3_data$q55i <- recode(merged_r3_data$q55i,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r3_data <- 
  merged_r3_data %>% 
  mutate(conf_just = replace(q55i, q55i >= 5, NA))

table(merged_r3_data$conf_just)
```

Question Number: Q65J
Question: How well or badly would you say the current government is handling the following matters, or haven’t
you heard enough about them to say: Fighting corruption in government?
Variable Label: Handling fighting corruption
Value Labels: 1=Very Badly, 2=Fairly Badly, 3=Fairly Well, 4=Very Well, 9=Don’t Know/Haven’t heard enough,
98=Refused to Answer, -1=Missing Data 
```{r}
table(merged_r3_data$q65j)
merged_r3_data$q65j <- as.numeric(merged_r3_data$q65j)

merged_r3_data <- 
  merged_r3_data %>% 
  mutate(fight_corruption = replace(q65j, q65j > 5 | q65j <=-1, NA))

table(merged_r3_data$fight_corruption)
```


Question Number: Q56D
Question: How many of the following people do you think are involved in corruption, or haven’t you heard enough
about them to say: National government officials?
Variable Label: Corruption: National government officials
Values: 0-3, 9, 98, -1
Value Labels: 0=None, 1=Some of them, 2=Most of them, 3=All of them, 9=Don’t Know, 98=Refused to Answer,
-1=Missing Data 
```{r}
table(merged_r3_data$q56d)

merged_r3_data$q56d <- as.numeric(merged_r3_data$q56d)

merged_r3_data$groups_corruption <- recode(merged_r3_data$q56d,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r3_data <- 
  merged_r3_data %>% 
  mutate(groups_corruption = replace(groups_corruption, groups_corruption >= 5, NA))

table(merged_r3_data$groups_corruption)
```


Question Number: Q47
Question: Overall, how satisfied are you with the way democracy works in [Ghana/Kenya/etc.]? Are you:
Variable Label: Satisfaction with democracy
Values: 0-4, 9, 98, -1
Value Labels: 0=My country is not a democracy, 1=Not at All Satisfied, 2=Not Very Satisfied, 3=Fairly Satisfied,
4=Very Satisfied, 9=Don’t Know, 98=Refused to Answer, -1=Missing Data 
```{r}
table(merged_r3_data$q47)
merged_r3_data$q47 <- as.numeric(merged_r3_data$q47)

merged_r3_data$sat_dem <- recode(merged_r3_data$q47,
                             "-1" = 99,
                             "0" = 99)

merged_r3_data <- 
  merged_r3_data %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA))

table(merged_r3_data$sat_dem)
```

Join
```{r}
conf_gov_afr_w3 <- merged_r3_data %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

conf_just_afr_w3 <- merged_r3_data %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

fight_corruption_afr_w3 <- merged_r3_data %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

groups_corruption_afr_w3 <- merged_r3_data %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

sat_dem_afr_w3 <- merged_r3_data %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

conf_gov_afr_w3 <- rename(conf_gov_afr_w3, scale = conf_gov)
conf_just_afr_w3 <- rename(conf_just_afr_w3, scale = conf_just)
fight_corruption_afr_w3 <- rename(fight_corruption_afr_w3, scale = fight_corruption)
groups_corruption_afr_w3 <- rename(groups_corruption_afr_w3, scale = groups_corruption)
sat_dem_afr_w3 <- rename(sat_dem_afr_w3, scale = sat_dem)

africa_w3_final <- conf_gov_afr_w3 %>%
  full_join(conf_just_afr_w3, by = c("country", "year", "ccode", "scale")) 

africa_w3_final <- africa_w3_final %>%
  full_join(fight_corruption_afr_w3, by = c("country", "year", "ccode", "scale")) 

africa_w3_final <- africa_w3_final %>%
  full_join(groups_corruption_afr_w3, by = c("country", "year", "ccode", "scale")) 

africa_w3_final <- africa_w3_final %>%
  full_join(sat_dem_afr_w3, by = c("country", "year", "ccode", "scale")) 

names(africa_w3_final)
africa_w3_final <- select(africa_w3_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))
```

Wave 4

```{r}
merged_r4_data <- read_sav("Data bases/Africanbarometer/merged_r4_data.sav")
names(merged_r4_data)
```
```{r}
merged_r4_data$country <- as.numeric(merged_r4_data$COUNTRY)
table(merged_r4_data$country)

merged_r4_data <- merged_r4_data %>%
  mutate(country = recode(country,
                          "1" = "Benin",
                          "2" = "Botswana",
                          "3" = "Burkina Faso",
                          "4" = "Cape Verde",
                          "5" = "Ghana",
                          "6" = "Kenya",
                          "7" = "Lesotho",
                          "8" = "Liberia",
                          "9" = "Madagascar",
                          "10" = "Malawi",
                          "11" = "Mali",
                          "12" = "Mozambique",
                          "13" = "Namibia",
                          "14" = "Nigeria",
                          "15" = "Senegal",
                          "16" = "South Africa",
                          "17" = "Tanzania",
                          "18" = "Uganda",
                          "19" = "Zambia",
                          "20" = "Zimbabwe"))

table(merged_r4_data$country)

# Create country code
merged_r4_data$ccode <- NA
merged_r4_data$ccode <- countrycode(merged_r4_data$country, origin = "country.name",
                                    destination = "cown", warn = TRUE)
```


```{r}
table(merged_r4_data$DATEINTR)

merged_r4_data$year <- format(as.Date(merged_r4_data$DATEINTR, format="%Y-%m-%d"),"%Y")

table(merged_r4_data$year)
table(merged_r4_data$year, merged_r4_data$country)
```

Question Number: Q49A
Question: How much do you trust each of the following, or haven’t you heard enough about them to say: The
President?
Variable Label: Trust president
Values: 0-3, 9, 998, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t know/Haven’t heard enough,
998=Refused to answer, -1=Missing data
```{r}
table(merged_r4_data$Q49A)
merged_r4_data$Q49A <- as.numeric(merged_r4_data$Q49A)

merged_r4_data$Q49A <- recode(merged_r4_data$Q49A,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r4_data <- 
  merged_r4_data %>% 
  mutate(conf_gov = replace(Q49A, Q49A >= 5, NA))

table(merged_r4_data$conf_gov)
```


Question Number: Q49H
Question: How much do you trust each of the following, or haven’t you heard enough about them to say: Courts of
law?
Variable Label: Trust courts of law
Values: 0-3, 9, 998, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t know/Haven’t heard enough,
998=Refused to answer, -1=Missing data
```{r}
table(merged_r4_data$Q49H)
merged_r4_data$Q49H <- as.numeric(merged_r4_data$Q49H)

merged_r4_data$Q49H <- recode(merged_r4_data$Q49H,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r4_data <- 
  merged_r4_data %>% 
  mutate(conf_just = replace(Q49H, Q49H >= 5, NA))

table(merged_r4_data$conf_just)
```

Question Number: Q57K
Question: How well or badly would you say the current government is handling the following matters, or haven’t
you heard enough to say: Fighting corruption in government?
Variable Label: Handling fighting corruption
Values: 1-4, 9, 998, -1
Value Labels: 1=Very badly, 2=Fairly badly
```{r}
table(merged_r4_data$Q57K)
merged_r4_data$Q57K <- as.numeric(merged_r4_data$Q57K)

merged_r4_data <- 
  merged_r4_data %>% 
  mutate(fight_corruption = replace(Q57K, Q57K > 5 | Q57K <=-1, NA))

table(merged_r4_data$fight_corruption)
```


Question Number: Q50D
Question: How many of the following people do you think are involved in corruption, or haven’t you heard enough
about them to say: Government Officials?
Variable Label: Corruption: government officials
Values: 0-3, 9, 998, -1
Value Labels: 0=None, 1=Some of them, 2=Most of them, 3=All of them, 9=Don’t know, 998=Refused to answer,
-1=Missing data
```{r}
table(merged_r4_data$Q50D)

merged_r4_data$Q50D <- as.numeric(merged_r4_data$Q50D)

merged_r4_data$groups_corruption <- recode(merged_r4_data$Q50D,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r4_data <- 
  merged_r4_data %>% 
  mutate(groups_corruption = replace(groups_corruption, groups_corruption >= 5, NA))

table(merged_r4_data$groups_corruption)
```


Question Number: Q43
Question: Overall, how satisfied are you with the way democracy works in [Ghana/Kenya/etc.]? Are you:
Variable Label: Satisfaction with democracy
Values: 0-4, 9, 998, -1
Value Labels: 0=My country is not a democracy, 1=Not at all satisfied, 2=Not very satisfied, 3=Fairly satisfied,
4=Very satisfied, 9=Don’t know, 998=Refused to answer, -1=Missing data
```{r}
table(merged_r4_data$Q43)

merged_r4_data$Q43 <- as.numeric(merged_r4_data$Q43)

merged_r4_data$sat_dem <- recode(merged_r4_data$Q43,
                             "-1" = 99,
                             "0" = 99)

merged_r4_data <- 
  merged_r4_data %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA))

table(merged_r4_data$sat_dem)
```

Join
```{r}
conf_gov_afr_w4 <- merged_r4_data %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

conf_just_afr_w4 <- merged_r4_data %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

fight_corruption_afr_w4 <- merged_r4_data %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

groups_corruption_afr_w4 <- merged_r4_data %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

sat_dem_afr_w4 <- merged_r4_data %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

conf_gov_afr_w4 <- rename(conf_gov_afr_w4, scale = conf_gov)
conf_just_afr_w4 <- rename(conf_just_afr_w4, scale = conf_just)
fight_corruption_afr_w4 <- rename(fight_corruption_afr_w4, scale = fight_corruption)
groups_corruption_afr_w4 <- rename(groups_corruption_afr_w4, scale = groups_corruption)
sat_dem_afr_w4 <- rename(sat_dem_afr_w4, scale = sat_dem)

africa_w4_final <- conf_gov_afr_w4 %>%
  full_join(conf_just_afr_w4, by = c("country", "year", "ccode", "scale")) 

africa_w4_final <- africa_w4_final %>%
  full_join(fight_corruption_afr_w4, by = c("country", "year", "ccode", "scale")) 

africa_w4_final <- africa_w4_final %>%
  full_join(groups_corruption_afr_w4, by = c("country", "year", "ccode", "scale")) 

africa_w4_final <- africa_w4_final %>%
  full_join(sat_dem_afr_w4, by = c("country", "year", "ccode", "scale")) 

names(africa_w4_final)
africa_w4_final <- select(africa_w4_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))

```

Wave 5

```{r}
merged_r5_data <- read_sav("Data bases/Africanbarometer/merged_r5_data.sav")
names(merged_r5_data)
```

```{r}
merged_r5_data$country <- as.numeric(merged_r5_data$COUNTRY_ALPHA)
table(merged_r5_data$country)

merged_r5_data <- merged_r5_data %>%
  mutate(country = recode(country,
                          "1" = "Algeria",
                          "2" = "Benin",
                          "3" = "Botswana",
                          "4" = "Burkina Faso",
                          "5" = "Burundi",
                          "6" = "Cameroon",
                          "7" = "Cape Verde",
                          "8" = "Cote d’Ivoire",
                          "9" = "Egypt",
                          "11" = "Ghana",
                          "12" = "Guinea",
                          "13" = "Kenya",
                          "14" = "Lesotho",
                          "15" = "Liberia",
                          "16" = "Madagascar",
                          "17" = "Malawi",
                          "18" = "Mali",
                          "19" = "Mauritius",
                          "20" = "Morocco",
                          "21" = "Mozambique",
                          "22" = "Namibia",
                          "23" = "Niger",
                          "24" = "Nigeria",
                          "25" = "Senegal",
                          "26" = "Sierra Leone",
                          "27" = "South Africa",
                          "28" = "Sudan",
                          "29" = "Swaziland",
                          "30" = "Tanzania",
                          "31" = "Togo",
                          "32" = "Tunisia",
                          "33" = "Uganda",
                          "34" = "Zambia",
                          "35" = "Zimbabwe"))

table(merged_r5_data$country)

# Create country code
merged_r5_data$ccode <- NA
merged_r5_data$ccode <- countrycode(merged_r5_data$country, origin = "country.name",
                                    destination = "cown", warn = TRUE)
```
```{r}
table(merged_r5_data$DATEINTR)

merged_r5_data$year <- format(as.Date(merged_r5_data$DATEINTR, format="%Y-%m-%d"),"%Y")

table(merged_r5_data$year)
table(merged_r5_data$year, merged_r5_data$country)
```

Question Number: Q59A
**Question: How much do you trust each of the following, or haven’t you heard enough about them to say:
The President/Prime Minister?
Variable Label: Trust key leadership figure (President/Prime Minister)
Values: 0-3, 9, 998, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t know/Haven’t heard enough,
997=Not asked, 998=Refused to answer, -1=Missing
```{r}
table(merged_r5_data$Q59A)
merged_r5_data$Q59A <- as.numeric(merged_r5_data$Q59A)

merged_r5_data$Q59A <- recode(merged_r5_data$Q59A,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r5_data <- 
  merged_r5_data %>% 
  mutate(conf_gov = replace(Q59A, Q59A >= 5, NA))

table(merged_r5_data$conf_gov)
```


Question Number: Q59J
Question: How much do you trust each of the following, or haven’t you heard enough about them to say:
Courts of law?
Variable Label: Trust courts of law
Values: 0-3, 9, 998, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t know/Haven’t heard enough,
998=Refused to answer, -1=Missing
```{r}
table(merged_r5_data$Q59J)
merged_r5_data$Q59J <- as.numeric(merged_r5_data$Q59J)

merged_r5_data$Q59J <- recode(merged_r5_data$Q59J,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r5_data <- 
  merged_r5_data %>% 
  mutate(conf_just = replace(Q59J, Q59J >= 5, NA))

table(merged_r5_data$conf_just)
```

Question Number: Q65K
Question: How well or badly would you say the current government is handling the following matters, or
haven’t you heard enough to say: Fighting corruption in government?
Variable Label: Handling fighting corruption
Values: 1-4, 9, 998, -1
Value Labels: 1=Very badly, 2=Fairly badly, 3=Fairly well, 4=Very well, 9=Don’t know/Haven’t heard enough,
998=Refused to answer, -1=Missing.
```{r}
table(merged_r5_data$Q65K)
merged_r5_data$Q65K <- as.numeric(merged_r5_data$Q65K)

merged_r5_data <- 
  merged_r5_data %>% 
  mutate(fight_corruption = replace(Q65K, Q65K > 5 | Q65K <=-1, NA))

table(merged_r5_data$fight_corruption)
```


Question Number: Q60C
Question: How many of the following people do you think are involved in corruption, or haven’t you heard
enough about them to say: Government Officials?
Values: 0-3, 9, 998, -1
Value Labels: 0=None, 1=Some of them, 2=Most of them, 3=All of them, 9=Don’t know, 998=Refused to answer,
-1=Missing data
```{r}
table(merged_r5_data$Q60C)

merged_r5_data$Q60C <- as.numeric(merged_r5_data$Q60C)

merged_r5_data$groups_corruption <- recode(merged_r5_data$Q60C,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r5_data <- 
  merged_r5_data %>% 
  mutate(groups_corruption = replace(groups_corruption, groups_corruption >= 5, NA))

table(merged_r5_data$groups_corruption)
```


Question Number: Q43
**Question: Overall, how satisfied are you with the way democracy works in the country? Are you:
Variable Label: Satisfaction with democracy
Values: 0-4, 9, 998, -1
**Value Labels: 0=the country is not a democracy, 1=Not at all satisfied, 2=Not very satisfied, 3=Fairly
satisfied, 4=Very satisfied, 9=Don’t know, 998=Refused to answer, -1=Missing
```{r}
table(merged_r5_data$Q43)

merged_r5_data$Q43 <- as.numeric(merged_r5_data$Q43)

merged_r5_data$sat_dem <- recode(merged_r5_data$Q43,
                             "-1" = 99,
                             "0" = 99)

merged_r5_data <- 
  merged_r5_data %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA))

table(merged_r5_data$sat_dem)
```

Join
```{r}
conf_gov_afr_w5 <- merged_r5_data %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

conf_just_afr_w5 <- merged_r5_data %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

fight_corruption_afr_w5 <- merged_r5_data %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

groups_corruption_afr_w5 <- merged_r5_data %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

sat_dem_afr_w5 <- merged_r5_data %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

conf_gov_afr_w5 <- rename(conf_gov_afr_w5, scale = conf_gov)
conf_just_afr_w5 <- rename(conf_just_afr_w5, scale = conf_just)
fight_corruption_afr_w5 <- rename(fight_corruption_afr_w5, scale = fight_corruption)
groups_corruption_afr_w5 <- rename(groups_corruption_afr_w5, scale = groups_corruption)
sat_dem_afr_w5 <- rename(sat_dem_afr_w5, scale = sat_dem)

africa_w5_final <- conf_gov_afr_w5 %>%
  full_join(conf_just_afr_w5, by = c("country", "year", "ccode", "scale")) 

africa_w5_final <- africa_w5_final %>%
  full_join(fight_corruption_afr_w5, by = c("country", "year", "ccode", "scale")) 

africa_w5_final <- africa_w5_final %>%
  full_join(groups_corruption_afr_w5, by = c("country", "year", "ccode", "scale")) 

africa_w5_final <- africa_w5_final %>%
  full_join(sat_dem_afr_w5, by = c("country", "year", "ccode", "scale")) 

names(africa_w5_final)
africa_w5_final <- select(africa_w5_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))

```

Wave 6
```{r}
merged_r6_data <- haven::read_sav("Data bases/Africanbarometer/merged_r6_data.sav", encoding="latin1")

merged_r6_data <- haven::read_sav("Data bases/Africanbarometer/merged_r6_data.sav", col_select = "Q29B", skip = 39618, n_max = 1)
names(merged_r5_data)
```

Wave 7
```{r}
merged_r7_data <- read_sav("Data bases/Africanbarometer/merged_r7_data.sav")
names(merged_r7_data)
```

```{r}
merged_r7_data$country <- as.numeric(merged_r7_data$COUNTRY)
table(merged_r7_data$country)

merged_r7_data <- merged_r7_data %>%
  mutate(country = recode(country,
                          "1" = "Benin",
                          "2" = "Botswana",
                          "3" = "Burkina Faso",
                          "4" = "Cape Verde",
                          "5" = "Cameroon",
                          "6" = "Cote d’Ivoire",
                          "7" = "Swaziland",
                          "8" = "Gabon",
                          "9" = "Gambia",
                          "10" = "Ghana",
                          "11" = "Guinea",
                          "12" = "Kenya",
                          "13" = "Lesotho",
                          "14" = "Liberia",
                          "15" = "Madagascar",
                          "16" = "Malawi",
                          "17" = "Mali",
                          "18" = "Mauritius",
                          "19" = "Morocco",
                          "20" = "Mozambique",
                          "21" = "Namibia",
                          "22" = "Niger",
                          "23" = "Nigeria",
                          "24" = "Sao Tomé and Príncipe",
                          "25" = "Senegal",
                          "26" = "Sierra Leone",
                          "27" = "South Africa",
                          "28" = "Sudan",
                          "29" = "Tanzania",
                          "30" = "Togo",
                          "31" = "Tunisia",
                          "32" = "Uganda",
                          "33" = "Zambia",
                          "34" = "Zimbabwe"))

table(merged_r7_data$country)

# Create country code
merged_r7_data$ccode <- NA
merged_r7_data$ccode <- countrycode(merged_r7_data$country, origin = "country.name",
                                    destination = "cown", warn = TRUE)
```
```{r}
table(merged_r7_data$DATEINTR)

merged_r7_data$year <- format(as.Date(merged_r7_data$DATEINTR, format="%Y-%m-%d"),"%Y")

table(merged_r7_data$year)
table(merged_r7_data$year, merged_r7_data$country)
```

Question Number: Q43A
Question: How much do you trust each of the following, or haven’t you heard enough about them to say:
The President?
Variable Label: Q43a. Trust president
Values: 0-3, 9, 8, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t know/Haven’t heard enough,
8=Refused to answer, -1=Missing 
```{r}
table(merged_r7_data$Q43A)
merged_r7_data$Q43A <- as.numeric(merged_r7_data$Q43A)

merged_r7_data$Q43A <- recode(merged_r7_data$Q43A,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r7_data <- 
  merged_r7_data %>% 
  mutate(conf_gov = replace(Q43A, Q43A >= 5, NA))

table(merged_r7_data$conf_gov)
```


Question Number: Q43I
Question: How much do you trust each of the following, or haven’t you heard enough about them to say:
Courts of law?
Variable Label: Q43i. Trust courts of law
Values: 0-3, 9, 8, -1
Value Labels: 0=Not at all, 1=Just a little, 2=Somewhat, 3=A lot, 9=Don’t know/Haven’t heard enough,
8=Refused to answer, -1=Missing 
```{r}
table(merged_r7_data$Q43I)
merged_r7_data$Q43I <- as.numeric(merged_r7_data$Q43I)

merged_r7_data$Q43I <- recode(merged_r7_data$Q43I,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r7_data <- 
  merged_r7_data %>% 
  mutate(conf_just = replace(Q43I, Q43I >= 5, NA))

table(merged_r7_data$conf_just)
```

Question Number: Q56K
Question: How well or badly would you say the current government is handling the following matters, or
haven’t you heard enough to say: Fighting corruption in government?
Variable Label: Q56k. Handling fighting corruption
Values: 1-4, 9, 8, -1
Value Labels: 1=Very badly, 2=Fairly badly, 3=Fairly well, 4=Very well, 9=Don’t know/Haven’t heard enough,
8=Refused to answer, -1=Missing
```{r}
table(merged_r7_data$Q56K)
merged_r7_data$Q56K <- as.numeric(merged_r7_data$Q56K)

merged_r7_data <- 
  merged_r7_data %>% 
  mutate(fight_corruption = replace(Q56K, Q56K > 5 | Q56K <=-1, NA))

table(merged_r7_data$fight_corruption)
```


Question Number: Q44C
Question: How many of the following people do you think are involved in corruption, or haven’t you heard
enough about them to say: Government officials?
Variable Label: Q44c. Corruption: government officials
Values: 0-3, 9, 8, -1
Value Labels: 0=None, 1=Some of them, 2=Most of them, 3=All of them, 9=Don’t know/Haven’t heard
enough, 8=Refused to answer, -1=Missing.
```{r}
table(merged_r7_data$Q44C)

merged_r7_data$Q44C <- as.numeric(merged_r7_data$Q44C)

merged_r7_data$groups_corruption <- recode(merged_r7_data$Q44C,
                             "0" = 1,
                             "1" = 2,
                             "2" = 3,
                             "3" = 4,
                             "-1" = 99)

merged_r7_data <- 
  merged_r7_data %>% 
  mutate(groups_corruption = replace(groups_corruption, groups_corruption >= 5, NA))

table(merged_r7_data$groups_corruption)
```


Question Number: Q36
Question: Overall, how satisfied are you with the way democracy works in [ENTER COUNTRY]? Are you:
Variable Label: Q36. Satisfaction with democracy
Values: 0-4, 9, 8, -1
Value Labels: 0=[Country] is not a democracy, 1=Not at all satisfied, 2=Not very satisfied, 3=Fairly satisfied,
4=Very satisfied, 9=Don’t know, 8=Refused to answer, -1=Missing 
```{r}
table(merged_r7_data$Q36)

merged_r7_data$Q36 <- as.numeric(merged_r7_data$Q36)

merged_r7_data$sat_dem <- recode(merged_r7_data$Q36,
                             "-1" = 99,
                             "0" = 99)

merged_r7_data <- 
  merged_r7_data %>% 
  mutate(sat_dem = replace(sat_dem, sat_dem >= 5, NA))

table(merged_r7_data$sat_dem)
```

```{r}
conf_gov_afr_w7 <- merged_r7_data %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

conf_just_afr_w7 <- merged_r7_data %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

fight_corruption_afr_w7 <- merged_r7_data %>%
  group_by(country, year, ccode, fight_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_fight_corr = round(cnt / sum(cnt), 3))

groups_corruption_afr_w7 <- merged_r7_data %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

sat_dem_afr_w7 <- merged_r7_data %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

conf_gov_afr_w7 <- rename(conf_gov_afr_w7, scale = conf_gov)
conf_just_afr_w7 <- rename(conf_just_afr_w7, scale = conf_just)
fight_corruption_afr_w7 <- rename(fight_corruption_afr_w7, scale = fight_corruption)
groups_corruption_afr_w7 <- rename(groups_corruption_afr_w7, scale = groups_corruption)
sat_dem_afr_w7 <- rename(sat_dem_afr_w7, scale = sat_dem)

africa_w7_final <- conf_gov_afr_w7 %>%
  full_join(conf_just_afr_w7, by = c("country", "year", "ccode", "scale")) 

africa_w7_final <- africa_w7_final %>%
  full_join(fight_corruption_afr_w7, by = c("country", "year", "ccode", "scale")) 

africa_w5_final <- africa_w7_final %>%
  full_join(groups_corruption_afr_w7, by = c("country", "year", "ccode", "scale")) 

africa_w7_final <- africa_w7_final %>%
  full_join(sat_dem_afr_w7, by = c("country", "year", "ccode", "scale")) 

names(africa_w7_final)
africa_w7_final <- select(africa_w7_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))
```

### Merge all Africabarometer
```{r}
africa_final <- africa_w1_final %>%
  full_join(africa_w2_final)

africa_final <- africa_final %>%
  full_join(africa_w3_final)

africa_final <- africa_final %>%
  full_join(africa_w4_final)

africa_final <- africa_final %>%
  full_join(africa_w5_final)

africa_final <- africa_final %>%
  full_join(africa_w7_final)

table(africa_final$country, africa_final$year)

```


# LAPOP
```{r}
lapop <- read_dta("Data bases/LAPOP/lapop.dta")
names(lapop)
```

```{r}
table(lapop$pais)
```


```{r}
lapop$country <- as.numeric(lapop$pais)
table(lapop$country)

lapop <- lapop %>%
  mutate(country = recode(country,
                          "1" = "Mexico",
                          "2" = "Guatemala",
                          "3" = "El Salvador",
                          "4" = "Honduras",
                          "5" = "Nicaragua",
                          "6" = "Costa Rica",
                          "7" = "Panama",
                          "8" = "Colombia",
                          "9" = "Ecuador",
                          "10" = "Bolivia",
                          "11" = "Peru",
                          "12" = "Paraguay",
                          "13" = "Chile",
                          "14" = "Uruguay",
                          "15" = "Brazil",
                          "16" = "Venezuela",
                          "17" = "Argentina",
                          "21" = "Dominican Republic",
                          "22" = "Haiti",
                          "23" = "Jamaica",
                          "24" = "Guyana",
                          "25" = "Trinidad and Tobago",
                          "26" = "Belize",
                          "27" = "Surinam",
                          "28" = "Bahamas",
                          "29" = "Barbados",
                          "40" = "USA",
                          "41" = "Canada"))

table(lapop$country)

# Create country code
lapop$ccode <- NA
lapop$ccode <- countrycode(lapop$country, origin = "country.name",
                                    destination = "cown", warn = TRUE)
```

b14
 ¿Hasta qué punto tiene confianza usted en Gobierno?
 To what extent do you trust the government?
1 Nada
2
3
4
5
6
7 Mucho
.a No sabe
.b No responde
.z No se le preguntó en este país o año
```{r}
table(lapop$b14)
lapop$b14 <- as.numeric(lapop$b14)

lapop$conf_gov <- recode(lapop$b14,
                     "1" = 1,
                     "2" = 1,
                     "3" = 2,
                     "4" = 2,
                     "5" = 3,
                     "6" = 4,
                     "7" = 4)

table(lapop$conf_gov)
```


b10a
 ¿Hasta qué punto tiene confianza en el sistema de justicia?
 To what extent do you trust the justice system?
 1 Nada
2
3
4
5
6
7 Mucho
.a No sabe
.b No responde
.z No se le preguntó en este país o año
```{r}
table(lapop$b10a)
lapop$b10a <- as.numeric(lapop$b10a)

lapop$conf_just <- recode(lapop$b10a,
                     "1" = 1,
                     "2" = 1,
                     "3" = 2,
                     "4" = 2,
                     "5" = 3,
                     "6" = 4,
                     "7" = 4)

table(lapop$conf_just)
```

pc2 corrupción ministros
pc2
1 Muy corruptos
2
3
4
5
6
7
8
9
10 Muy honrados
.a No sabe
.c No Aplica
.z No se le preguntó en este país o año
```{r}
table(lapop$pc2)

lapop$pc2 <- as.numeric(lapop$pc2)

lapop$groups_corruption <- recode(lapop$pc2,
                             "10" = 1,
                             "9" = 1,
                             "8" = 1,
                             "7" = 2,
                             "6" = 2,
                             "5" = 3,
                             "4" = 3,
                             "3" = 4,
                             "2" = 4,
                             "1" = 4)

table(lapop$groups_corruption)
```


satisfacción democracia
pn4
1 Muy satisfecho(a)
2 Satisfecho(a)
3 Insatisfecho(a)
4 Muy insatisfecho(a)
```{r}
table(lapop$pn4)

lapop$pn4 <- as.numeric(lapop$pn4)

lapop$sat_dem <- recode(lapop$pn4,
                        "4" = 1,
                        "3" = 2,
                        "2" = 3,
                        "1" = 4)

table(lapop$sat_dem)
```

```{r}
conf_gov_lapop <- lapop %>%
  group_by(country, year, ccode, conf_gov) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_gov = round(cnt / sum(cnt), 3))

conf_just_lapop <- lapop %>%
  group_by(country, year, ccode, conf_just) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_conf_just = round(cnt / sum(cnt), 3))

groups_corruption_lapop <- lapop %>%
  group_by(country, year, ccode, groups_corruption) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_groups_corr = round(cnt / sum(cnt), 3))

sat_dem_lapop <- lapop %>%
  group_by(country, year, ccode, sat_dem) %>%
  summarize(cnt = n()) %>% # add percentages
  drop_na() %>%
  mutate(per_sat_dem = round(cnt / sum(cnt), 3))

conf_gov_lapop <- rename(conf_gov_lapop, scale = conf_gov)
conf_just_lapop <- rename(conf_just_lapop, scale = conf_just)
groups_corruption_lapop <- rename(groups_corruption_lapop, scale = groups_corruption)
sat_dem_lapop <- rename(sat_dem_lapop, scale = sat_dem)

lapop_final <- conf_gov_lapop %>%
  full_join(conf_just_lapop, by = c("country", "year", "ccode", "scale")) 

lapop_final <- lapop_final %>%
  full_join(groups_corruption_lapop, by = c("country", "year", "ccode", "scale")) 

lapop_final <- lapop_final %>%
  full_join(sat_dem_lapop, by = c("country", "year", "ccode", "scale")) 

names(lapop_final)
lapop_final <- select(lapop_final, -c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))
```

# Latinobarometer

```{r}
conf_just_latinobarometro <- read_excel("Data bases/Latinobarómetro/conf_just_latinobarometro.xlsx")
sat_dem_latinobarometro <- read_excel("Data bases/Latinobarómetro/sat_dem_latinobarometro.xlsx")
extent_corruption_latinobarometro <- read_excel("Data bases/Latinobarómetro/extent_corruption_latinobarometro.xlsx")

conf_gov_latinobarometro <- read_excel("Data bases/Latinobarómetro/conf_gov_latinobarometro.xlsx")
fight_corruption_latinobarometro <- read_excel("Data bases/Latinobarómetro/fight_corruption_latinobarometro.xlsx")
```

# Join all databases

africa_final 
```{r}
table(africa_final$country, africa_final$year)
```
arab_final
```{r}
table(arab_final$country, arab_final$year)
```
lapop_final
```{r}
table(lapop_final$country, lapop_final$year)
```
wvs_final
```{r}
table(wvs_final$country, wvs_final$year)
```

```{r}
africa_final$year <- as.numeric(africa_final$year)
arab_final$year <- as.numeric(arab_final$year)

final_db <- africa_final %>%
  full_join(arab_final)

final_db <- final_db %>%
  full_join(lapop_final)

final_db <- final_db %>%
  full_join(wvs_final) %>%
  select(-c(cnt.x, cnt.y, cnt.x.x, cnt.y.y))

rm(list= ls()[!(ls() %in% c("africa_final","arab_final", "lapop_final", "wvs_final", "final_db"))])

table(final_db$country)
names(final_db)
```

Save in excel
```{r}
write_xlsx(final_db,"final_db.xlsx")
```


# Organize the data in long format

## First variable: corruption perception

A mix between per_ext_corr, per_fight_corr, per_groups_corr, and per_scale_corr

Only scale == 4

### per_ext_corr

Africabarometer
```{r}
extent_corruption_africa <- afr_w1_extent_corruption

# Create variable Sample
extent_corruption_africa <- extent_corruption_africa %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4

extent_corruption_africa <- extent_corruption_africa %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_ext_corr)

extent_corruption_africa$item <- "extent_corruption"
extent_corruption_africa$project <- "africabarometer"
head(extent_corruption_africa)

#extent_corruption_africa <- extent_corruption_africa %>%
#  rename(response = per_ext_corr)

```


Arab Barometer
```{r}
extent_corruption_arab <- arab_w4_extent_corruption %>%
  full_join(arab_w5_extent_corruption)

extent_corruption_arab <- extent_corruption_arab %>%
  full_join(arab_w6_extent_corruption)

# Create variable Sample
extent_corruption_arab <- extent_corruption_arab %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4

extent_corruption_arab <- extent_corruption_arab %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_ext_corr)

extent_corruption_arab$item <- "extent_corruption"
extent_corruption_arab$project <- "arabbarometer"
head(extent_corruption_arab)
```

LAPOP only has groups_corruption

WVS
```{r}
# Create variable Sample
extent_corruption_wvs <- wvs_extent_corruption %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
extent_corruption_wvs <- extent_corruption_wvs %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_extent_corr)

extent_corruption_wvs$item <- "extent_corruption"
extent_corruption_wvs$project <- "wvs"
head(extent_corruption_wvs)
```

Latinobarometro
```{r}
# Create variable Sample
extent_corruption_latinobarometro <- extent_corruption_latinobarometro %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4

extent_corruption_latinobarometro <- extent_corruption_latinobarometro %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_ext_corr)

extent_corruption_latinobarometro$item <- "extent_corruption"
extent_corruption_latinobarometro$project <- "latinobarometro"
head(extent_corruption_latinobarometro)
```

### per_fight_corr

Africabarometer
```{r}
fight_corruption_africa <- afr_w1_fight_corruption %>%
  full_join(fight_corruption_afr_w2)

fight_corruption_africa <- fight_corruption_africa %>%
  full_join(fight_corruption_afr_w3)

fight_corruption_africa <- fight_corruption_africa %>%
  full_join(fight_corruption_afr_w4)

fight_corruption_africa <- fight_corruption_africa %>%
  full_join(fight_corruption_afr_w5)

fight_corruption_africa <- fight_corruption_africa %>%
  full_join(fight_corruption_afr_w7)

# Create variable Sample
fight_corruption_africa <- fight_corruption_africa %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
fight_corruption_africa <- fight_corruption_africa %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_fight_corr)

fight_corruption_africa$item <- "fight_corruption"
fight_corruption_africa$project <- "africabarometer"
head(fight_corruption_africa)
```

Arab barometer

```{r}
fight_corruption_arab <- arab_w1_fight_corruption %>%
  full_join(arab_w2_fight_corruption)

fight_corruption_arab <- fight_corruption_arab %>%
  full_join(arab_w3_fight_corruption)

fight_corruption_arab <- fight_corruption_arab %>%
  full_join(arab_w4_fight_corruption)

fight_corruption_arab <- fight_corruption_arab %>%
  full_join(arab_w5_fight_corruption)

# Create variable Sample
fight_corruption_arab <- fight_corruption_arab %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
fight_corruption_arab <- fight_corruption_arab %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_fight_corr)

fight_corruption_arab$item <- "fight_corruption"
fight_corruption_arab$project <- "arabbarometer"

head(fight_corruption_arab)
```

WVS doesn't have fight corruption

Latinobarometro
```{r}
# Create variable Sample
fight_corruption_latinobarometro <- fight_corruption_latinobarometro %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
fight_corruption_latinobarometro <- fight_corruption_latinobarometro %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_fight_corr)

fight_corruption_latinobarometro$item <- "fight_corruption"
fight_corruption_latinobarometro$project <- "latinobarometro"
head(fight_corruption_latinobarometro)
```

### per_groups_corr

Africabarometer
```{r}
groups_corruption_africa <- afr_w1_groups_corruption %>%
  full_join(groups_corruption_afr_w2)

groups_corruption_africa <- groups_corruption_africa %>%
  full_join(groups_corruption_afr_w3)

groups_corruption_africa <- groups_corruption_africa %>%
  full_join(groups_corruption_afr_w4)

groups_corruption_africa <- groups_corruption_africa %>%
  full_join(groups_corruption_afr_w5)

groups_corruption_africa <- groups_corruption_africa %>%
  full_join(groups_corruption_afr_w7)

# Create variable Sample
groups_corruption_africa <- groups_corruption_africa %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
groups_corruption_africa <- groups_corruption_africa %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_groups_corr)

groups_corruption_africa$item <- "groups_corruption"
groups_corruption_africa$project <- "africabarometer"
head(groups_corruption_africa)
```

Arabbarometer doesn't have groups corruption

LAPOP
```{r}
# Create variable Sample
groups_corruption_lapop_filter <- groups_corruption_lapop %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
groups_corruption_lapop_filter <- groups_corruption_lapop_filter %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_groups_corr)

groups_corruption_lapop_filter$item <- "groups_corruption"
groups_corruption_lapop_filter$project <- "lapop"
head(groups_corruption_lapop_filter)
```

WVS
```{r}
# Create variable Sample
groups_corruption_wvs <- wvs_groups_corruption %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
groups_corruption_wvs <- groups_corruption_wvs %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_groups_corr)

groups_corruption_wvs$item <- "groups_corruption"
groups_corruption_wvs$project <- "wvs"
head(groups_corruption_wvs)
```

### per_scale_corr

Only WVS has perr_scale_corr
```{r}
# Create variable Sample
scale_corruption_wvs <- wvs_scale_corruption %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
scale_corruption_wvs <- scale_corruption_wvs %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_scale_corr)

scale_corruption_wvs$item <- "scale_corruption"
scale_corruption_wvs$project <- "wvs"
head(scale_corruption_wvs)
```

## Join all the corruption datasets
```{r}
corruption_final <- extent_corruption_africa %>%
  full_join(extent_corruption_arab)

corruption_final$year <- as.numeric(corruption_final$year)
extent_corruption_wvs$year <- as.numeric(extent_corruption_wvs$year)
corruption_final <- corruption_final %>%
  full_join(extent_corruption_wvs)

fight_corruption_africa$year <- as.numeric(fight_corruption_africa$year)
corruption_final <- corruption_final %>%
  full_join(fight_corruption_africa)

fight_corruption_arab$year <- as.numeric(fight_corruption_arab$year)
corruption_final <- corruption_final %>%
  full_join(fight_corruption_arab)

groups_corruption_lapop_filter$year <- as.numeric(groups_corruption_lapop_filter$year)
corruption_final <- corruption_final %>%
  full_join(groups_corruption_lapop_filter)

groups_corruption_wvs$year <- as.numeric(groups_corruption_wvs$year)
corruption_final <- corruption_final %>%
  full_join(groups_corruption_wvs)

scale_corruption_wvs$year <- as.numeric(scale_corruption_wvs$year)
corruption_final <- corruption_final %>%
  full_join(scale_corruption_wvs)

corruption_final <- corruption_final %>%
  full_join(extent_corruption_latinobarometro)

corruption_final <- corruption_final %>%
  full_join(fight_corruption_latinobarometro)
```

Save in excel
```{r}
write_xlsx(corruption_final,"corruption_final_v2.xlsx")
```

# Government trust

Africabarometer
```{r}
conf_gov_africa <- afr_w1_conf_gov %>%
  full_join(conf_gov_afr_w2)

conf_gov_africa <- conf_gov_africa %>%
  full_join(conf_gov_afr_w3)

conf_gov_africa <- conf_gov_africa %>%
  full_join(conf_gov_afr_w4)

conf_gov_africa <- conf_gov_africa %>%
  full_join(conf_gov_afr_w5)

conf_gov_africa <- conf_gov_africa %>%
  full_join(conf_gov_afr_w7)

# Create variable Sample
conf_gov_africa <- conf_gov_africa %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_gov_africa <- conf_gov_africa %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_gov)

conf_gov_africa$item <- "confidence_government"
conf_gov_africa$project <- "africabarometer"
head(conf_gov_africa)
```
Arab Barometer
```{r}
conf_gov_arab <- arab_w1_conf_gov %>%
  full_join(arab_w2_conf_gov)

conf_gov_arab <- conf_gov_arab %>%
  full_join(arab_w3_conf_gov)

conf_gov_arab <- conf_gov_arab %>%
  full_join(arab_w4_conf_gov)

conf_gov_arab <- conf_gov_arab %>%
  full_join(arab_w5_conf_gov)

conf_gov_arab <- conf_gov_arab %>%
  full_join(arab_w6_conf_gov)

# Create variable Sample
conf_gov_arab <- conf_gov_arab %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_gov_arab <- conf_gov_arab %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_gov)

conf_gov_arab$item <- "confidence_government"
conf_gov_arab$project <- "arabbarometer"
head(conf_gov_arab)
```
LAPOP
```{r}
# Create variable Sample
conf_gov_lapop <- conf_gov_lapop %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_gov_lapop <- conf_gov_lapop %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_gov)

conf_gov_lapop$item <- "confidence_government"
conf_gov_lapop$project <- "lapop"
head(conf_gov_lapop)
```
Latinobarometro
```{r}
# Create variable Sample
conf_gov_latinobarometro <- conf_gov_latinobarometro %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_gov_latinobarometro <- conf_gov_latinobarometro %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_gov)

conf_gov_latinobarometro$item <- "confidence_government"
conf_gov_latinobarometro$project <- "latinobarometro"
head(conf_gov_latinobarometro)
```
WVS
```{r}
# Create variable Sample
conf_gov_wvs <- wvs_conf_gov %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_gov_wvs <- conf_gov_wvs %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_gov)

conf_gov_wvs$item <- "confidence_government"
conf_gov_wvs$project <- "wvs"
head(conf_gov_wvs)
```
Join all databases
```{r}
conf_gov_final <- conf_gov_africa %>%
  full_join(conf_gov_arab)

conf_gov_final$year <- as.numeric(conf_gov_final$year)
conf_gov_final <- conf_gov_final %>%
  full_join(conf_gov_lapop)

conf_gov_final <- conf_gov_final %>%
  full_join(conf_gov_latinobarometro)

conf_gov_final <- conf_gov_final %>%
  full_join(conf_gov_wvs)

```

Save in excel
```{r}
write_xlsx(conf_gov_final,"conf_gov_final.xlsx")
```

# Judiciary trust

Africabarometer
```{r}
conf_just_africa <- afr_w1_conf_just %>%
  full_join(conf_just_afr_w2)

conf_just_africa <- conf_just_africa %>%
  full_join(conf_just_afr_w3)

conf_just_africa <- conf_just_africa %>%
  full_join(conf_just_afr_w4)

conf_just_africa <- conf_just_africa %>%
  full_join(conf_just_afr_w5)

conf_just_africa <- conf_just_africa %>%
  full_join(conf_just_afr_w7)

# Create variable Sample
conf_just_africa <- conf_just_africa %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_just_africa <- conf_just_africa %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_just)

conf_just_africa$item <- "confidence_justice"
conf_just_africa$project <- "africabarometer"
head(conf_just_africa)
```
Arab Barometer
```{r}
conf_just_arab <- arab_w1_conf_just %>%
  full_join(arab_w2_conf_just)

conf_just_arab <- conf_just_arab %>%
  full_join(arab_w4_conf_just)

conf_just_arab <- conf_just_arab %>%
  full_join(arab_w5_conf_just)

conf_just_arab <- conf_just_arab %>%
  full_join(arab_w6_conf_just)

# Create variable Sample
conf_just_arab <- conf_just_arab %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_just_arab <- conf_just_arab %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_just)

conf_just_arab$item <- "confidence_justice"
conf_just_arab$project <- "arabbarometer"
head(conf_just_arab)
```
LAPOP
```{r}
# Create variable Sample
conf_just_lapop <- conf_just_lapop %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_just_lapop <- conf_just_lapop %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_just)

conf_just_lapop$item <- "confidence_justice"
conf_just_lapop$project <- "lapop"
head(conf_just_lapop)
```
Latinobarometro
```{r}
# Create variable Sample
conf_just_latinobarometro <- conf_just_latinobarometro %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_just_latinobarometro <- conf_just_latinobarometro %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_just)

conf_just_latinobarometro$item <- "confidence_justice"
conf_just_latinobarometro$project <- "latinobarometro"
head(conf_just_latinobarometro)
```
WVS
```{r}
# Create variable Sample
conf_just_wvs <- wvs_conf_just %>%
  group_by(country) %>%
  mutate(uni=length(unique(year))) %>%
  group_by(country, year) %>%
  mutate(sample =sum(cnt)) %>%
  ungroup %>%
  select(-uni)

# Keep only scale == 4
conf_just_wvs <- conf_just_wvs %>%
  filter(scale == 4) %>%
  select(-c(cnt)) %>%
  rename(response = per_conf_just)

conf_just_wvs$item <- "confidence_justice"
conf_just_wvs$project <- "wvs"
head(conf_just_wvs)
```

Join with TJ database
```{r}
#Add ccodes to other databases
corruption_est <- read_csv("corruption_est.csv")

corruption_est$country[corruption_est$country == "Brasil"] <- "Brazil"
corruption_est$country[corruption_est$country == "México"] <- "Mexico"

corruption_est$ccode <- countrycode(corruption_est$country, origin = "country.name",
                             destination = "cown", warn = TRUE)


confidence_government_est <- read_csv("confidence_government_est.csv")
confidence_government_est$country[confidence_government_est$country == "Brasil"] <- "Brazil"
confidence_government_est$country[confidence_government_est$country == "México"] <- "Mexico"
confidence_government_est$ccode <- countrycode(confidence_government_est$country, origin = "country.name",
                             destination = "cown", warn = TRUE)

confidence_jud <- read_csv("confidence_jud.csv")
confidence_jud$country[confidence_jud$country == "Brasil"] <- "Brazil"
confidence_jud$country[confidence_jud$country == "México"] <- "Mexico"
confidence_jud$ccode <- countrycode(confidence_jud$country, origin = "country.name",
                             destination = "cown", warn = TRUE)


tj <- read_excel("tj_final.xlsx")
tj <- tj %>% distinct(ccode_year, .keep_all = TRUE)

tj_final <- tj %>%
  left_join(corruption_est, by = c("ccode", "year")) %>%
  rename(corr_est = data, first_yr_cor = First_yr) %>%
  select(-c(data_u95, data_l95, data_sd))

tj_final <- tj_final %>%
  left_join(confidence_government_est, by = c("ccode", "year")) %>%
  rename(conf_gov_est = data, first_yr_conf_gov = First_yr) %>%
  select(-c(data_u95, data_l95, data_sd))

tj_final <- tj_final %>%
  left_join(confidence_jud, by = c("ccode", "year")) %>%
  rename(conf_jud_est = data, first_yr_conf_jud = First_yr) %>%
  select(-c(data_u95, data_l95, data_sd, country.y, country.x.x, country.y.y)) %>%
  drop_na(ccode)

tj_filtered <- filter(tj_final, inclusion_final_db == 1)

tj_filtered <- tj_filtered %>% distinct(ccode_year, .keep_all = TRUE) %>%
  rename(country = country.x)

write_xlsx(tj_filtered,"tj_filtered.xlsx")
```

Identify those countries with no information for conf_jud_est (most populated variable)
```{r}
tj_clean <- tj_filtered %>%
  group_by(country) %>%
  mutate(conf_jud_mean = mean(conf_jud_est,  na.rm = TRUE)) %>%
  drop_na(conf_jud_mean) %>%
  select(-c(conf_jud_mean))

# Plot this
data_surveys <- panelview(country ~ treated, data = tj_clean,
                       index = c("country", "year"), main = "",
                       axis.lab.gap = c(2,0), xlab="", ylab="",
           legend.labs = c("Post-Transition", "Post-TJ", "Pre-Transition")) +
   theme_minimal() +
   theme(legend.title = element_blank(),
         legend.position = c("bottom"),
         plot.title = element_text(hjust = 0.5))

data_surveys
```


DID using did package
```{r}
set.seed(1814)
library(did)

# Make plots!

ggplot(tj_filtered, aes(x = factor(tj_in_democracy), y = conf_gov_est)) +
  stat_summary(geom = "pointrange", size = 1, color = "red",
               fun.data = "mean_se", fun.args = list(mult = 1.96)) +
  facet_wrap(vars(treated))
```

Estimating group ATE
```{r message=FALSE, warning=FALSE}
# estimate group-time average treatment effects using att_gt method
library(did)

tj_filtered <- tj_filtered %>%
  mutate(firsttreat = if_else(is.na(firsttreat), 0, firsttreat)) # 0 for nontreated

# Add world development indicators from WDI package
library(remotes)
install_github('vincentarelbundock/WDI')
gdp <- WDI(country = "all", indicator = "5.51.01.10.gdp", start = 1970, end = 2021)

attgt_conf_gov <- att_gt(yname = "conf_gov_est",
                        tname = "year",
                        idname = "ccode",
                        gname = "firsttreat",
                        xformla = ~polity + hdi,
                        data = tj_filtered,
                        control_group = "notyettreated"
                        )


# summarize the results
summary(attgt_conf_gov)
```


```{r}
# plot the results
# set ylim so that all plots have the same scale along y-axis
ggdid(attgt_conf_gov, ylim = c(-.3,.3))
```
```{r}
# aggregate the group-time average treatment effects
mw.dyn <- aggte(attgt_conf_gov, type = "dynamic", na.rm = TRUE)
summary(mw.dyn)
ggdid(mw.dyn, ylim = c(-4,4))
```

One potential issue with these dynamic effect estimators is that the composition of the groups changes with different lengths of exposure in the event study plots. 
One way to combat this is to balance the sample by (i) only including groups that are exposed to the treatment for at least a certain number of time periods and (ii) only look at dynamic effects in those time periods.
```{r}
mw.dyn.balance <- aggte(attgt_conf_gov, type = "dynamic", balance_e=2, na.rm = TRUE)
summary(mw.dyn.balance)
```

```{r}
ggdid(attgt_conf_gov, ylim = c(-0.2,0.2))
```

```{r}
summary(mw.dyn)

data_plot <- tidy(mw.dyn)

plot <- data_plot %>% 
    mutate(ymin_ptwise = estimate + 1.96*std.error,
           ymax_ptwise = estimate - 1.96*std.error)%>%
  ggplot(aes(x=event.time, y =estimate)) +
  geom_pointrange(aes(ymin = ymin_ptwise, ymax = ymax_ptwise))+ 
  geom_hline(yintercept =0) +
  xlab("Event Time") + ylab("Estimate") 
  #ggtitle("Effect of the implementation of TJ procedures on trust in government")

plot
```

Dynamic effects and event studies

```{r}
agg.es <- aggte(attgt_conf_gov, type = "dynamic", na.rm = TRUE)
summary(agg.es)
```

```{r}
ggdid(agg.es)
```

Group specific effects
```{r}
agg.gs <- aggte(attgt_conf_gov, type = "group", na.rm = TRUE)
summary(agg.gs)
```

```{r}
ggdid(agg.gs)
```

Calendar time effects
```{r}
agg.ct <- aggte(attgt_conf_gov, type = "calendar", na.rm = TRUE)
summary(agg.ct)
```

```{r}
ggdid(agg.ct)
```

With corruption as dependent variable

```{r}
corruption_attgt <- att_gt(yname = "corr_est",
                        tname = "year",
                        idname = "ccode",
                        gname = "firsttreat",
                        xformla = ~1,
                        data = tj_filtered,
                        control_group = "notyettreated"
                        )


# summarize the results
summary(corruption_attgt)
```

```{r}
# plot the results
ggdid(corruption_attgt)
```

Event-study parameters
```{r}
mw.dyn2 <- aggte(corruption_attgt, type = "dynamic", na.rm = TRUE)

data_plot2 <- tidy(mw.dyn2)

plot2 <- data_plot2 %>% 
    mutate(ymin_ptwise = estimate + 1.96*std.error,
           ymax_ptwise = estimate - 1.96*std.error)%>%
  ggplot(aes(x=event.time, y =estimate)) +
  geom_pointrange(aes(ymin = ymin_ptwise, ymax = ymax_ptwise))+ 
  geom_hline(yintercept =0) +
  xlab("Event Time") + ylab("Estimate") +
  xlim(c(-20,20)) 

plot2
```

Dynamic
```{r}
ggdid(mw.dyn2, ylim = c(-.10,.10))
```

```{r}
mw.dyn.balance2 <- aggte(corruption_attgt, type = "dynamic", balance_e=1)
ggdid(mw.dyn.balance2, ylim = c(-.1,.1))
```

Simple aggregation
```{r}
agg.simple2 <- aggte(corruption_attgt, type = "simple")
summary(agg.simple2)
```


Dynamic effects
```{r}
agg.es2 <- aggte(corruption_attgt, type = "dynamic")
ggdid(agg.es2)
```

Group specific effects
```{r}
agg.gs2 <- aggte(corruption_attgt, type = "group")
ggdid(agg.gs2, xlim = c(-.5,.5))
```

Calendar time effects
```{r}
agg.ct2 <- aggte(corruption_attgt, type = "calendar")
ggdid(agg.ct2)
```
Interaction between treatment and corruption
```{r}
# Separate the sample between low perception of corruption and high?

low_corruption <- tj_filtered %>%
  filter(corr_est <= 0)

high_corruption <- tj_filtered %>%
  filter(corr_est >= 0)

interaction_lc <- att_gt(yname = "conf_gov_est",
                        tname = "year",
                        idname = "ccode",
                        gname = "firsttreat",
                        xformla = ~1,
                        data = low_corruption,
                        control_group = "notyettreated"
                        )

interaction_hg <- att_gt(yname = "conf_gov_est",
                        tname = "year",
                        idname = "ccode",
                        gname = "firsttreat",
                        xformla = ~1,
                        data = high_corruption,
                        control_group = "notyettreated"
                        )


# Simple aggregation

agg_lc <- aggte(interaction_lc, type = "simple")
agg_hg <- aggte(interaction_hg, type = "simple", na.rm = TRUE)

tidy_agg_lc<- tidy(agg_lc)
tidy_agg_hg <- tidy(agg_hg)

summary(agg_lc)
summary(agg_hg)

```



Paralel trends
```{r}
paralell_trends <- tj_filtered %>%
  mutate(Treated = factor(treated, labels = c("Non Treated", "Treated"))) %>%
  group_by(Treated, year) %>%
  summarise(mean_corruption = mean(corr_est,  na.rm = TRUE),
            se_corruption = sd(mean_corruption) / sqrt(n()),
            upper = mean_corruption + (1.96 * mean_corruption),
            lower = mean_corruption + (-1.96 * mean_corruption))

# Figure 4 on manuscript
ggplot(paralell_trends, aes(x = year, y = mean_corruption, color = Treated)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), size = 0.5) +
  geom_line(aes(group = Treated)) + 
  scale_color_manual(values=c("#A6ACAF", "#17202A")) +
  theme_bw() +
  labs(x = "Year", y = "Mean Perception of Corruption") +
  xlim(c(1994,2021)) 
```


Trends for countries treated in the same year
```{r}
table(tj_filtered$firsttreat) #maybe 2005 could be a good year

trends_2005 <- tj_filtered %>%
  filter(firsttreat == 2005 | firsttreat == 0) #along with non-treated

paralell_trends_2005 <- trends_2005 %>%
  mutate(Treated = factor(firsttreat, labels = c("Non Treated", "Treated"))) %>%
  group_by(Treated, year) %>%
  summarise(mean_corruption = mean(conf_gov_est, na.rm = TRUE),
            se_corruption = sd(mean_corruption) / sqrt(n()),
            upper = mean_corruption + (1.96 * mean_corruption),
            lower = mean_corruption + (-1.96 * mean_corruption))

# Figure 4 on manuscript
ggplot(paralell_trends_2005, aes(x = year, y = mean_corruption, color = Treated)) +
  geom_point(aes(y = mean_corruption), size = 0.5) +
  geom_line(aes(group = Treated)) + 
  scale_color_manual(values=c("#A6ACAF", "#17202A")) +
  theme_bw() +
  labs(x = "Year", y = "Mean Perception of Corruption") +
  ylim(c(-1,1)) +
  scale_x_continuous(limits=c(1994,2021), breaks=seq(1994,2021, by = 3)) +
  geom_vline(xintercept = 2005, linetype = "dotted") +
  geom_text(aes(x=2004, label="Implementation", y= 0.8), 
            color = "#A6ACAF", angle=90, vjust = 1.2, size = 3)
```


https://lost-stats.github.io/Model_Estimation/Research_Design/event_study.html
```{r}
library(data.table) ## For some minor data wrangling
library(fixest)     ## NB: Requires version >=0.9.0

tj_filtered[, time_to_treat := ifelse(treated==1, year - `firsttreat`, 0)]

mod_twfe <- feols(conf_gov_est ~ 
                    i(time_to_treat, treated) + ## Our key interaction: time × treatment status
                    regime_polity5  |## Other controls
                    country + year,  ## FEs
                  cluster = ~country,   ## Clustered SEs
                  data = tj_filtered)

iplot(mod_twfe, 
      xlab = 'Time to treatment',
      main = 'Event study: Staggered treatment (TWFE)')
```
```{r}
# Following Sun and Abraham, we give our never-treated units a fake "treatment"
# date far outside the relevant study period.
tj_filtered[, year_treated := ifelse(treated==0, 10000, `firsttreat`)]

# Now we re-run our model from earlier, but this time swapping out 
# `i(time_to_treat, treat, ref = -1)` for `sunab(year_treated, year)`.
# See `?sunab`.
mod_sa <- feols(conf_gov_est ~ sunab(year_treated, year) + ## The only thing that's changed
                  regime_polity5 |
                  country + year,
	       cluster = ~country,
	       data = tj_filtered)
```











# Panel view
```{r}
db_final <- read_excel("db_final.xlsx")

panel_figure <- panelview(inclusion_final ~ treatment_post_dem, data = db_final,
                       index = c("country", "year"), main = "",
                       axis.lab.gap = c(2,0), xlab="", ylab="",
           legend.labs = c("Post-Transition", "Post-TJ", "Pre-Transition")) +
   theme_minimal() +
   theme(legend.title = element_blank(),
         legend.position = c("bottom"),
         plot.title = element_text(hjust = 0.5))
panel_figure


# Subset db_final to get a figure that fits into beamer
db_final_subset <- db_final %>%
  filter(country %in% c("Argentina", "Bolivia", "Burkina Faso", "DR Congo",
                      "El Salvador", "Ethiopia", "Guinea", "Kenya", "Macedonia",
                      "Mozambique", "Niger", "Panama", "Romania", "Senegal",
                      "Tanzania", "Zimbabwe")) 

panel_figure2 <- panelview(inclusion_final ~ treatment_post_dem, data = db_final_subset,
                       index = c("country", "year"), main = "",
                       axis.lab.gap = c(2,0), xlab="", ylab="",
           legend.labs = c("Post-Transition/Conflict", "Post-TJ", "Pre-Transition/Conflict")) +
   theme_minimal() +
   theme(legend.title = element_blank(),
         legend.position = c("bottom"),
         plot.title = element_text(hjust = 0.5))
panel_figure2
```







http://www.princeton.edu/~otorres/DID101R.pdf

https://lost-stats.github.io/Model_Estimation/Research_Design/event_study.html

https://cran.r-project.org/web/packages/did/vignettes/did-basics.html

https://cran.r-project.org/web/packages/staggered/readme/README.html

# Create a dummy variable to indicate the time when the treatment started. Lets
assume that treatment started in 1994. In this case, years before 1994 will have a
value of 0 and 1994+ a 1. If you already have this skip this step.
mydata$time = ifelse(mydata$year >= 1994, 1, 0)
# Create a dummy variable to identify the group exposed to the treatment. In this
example lets assumed that countries with code 5,6, and 7 were treated (=1).
Countries 1-4 were not treated (=0). If you already have this skip this step.
mydata$treated = ifelse(mydata$country == "E" |
mydata$country == "F" |
mydata$country == "G", 1, 0)
# Create an interaction between time and treated. We will call this interaction
‘did’.
mydata$did = mydata$time * mydata$treated
